[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
The value for en route ATFM delay per flight presented here is subsequent to the NM post operations delay attribution process.
:::
::::


### NSA's assessment of capacity performance
The Ukrainian war has had a significant impact, in both operational and economic context of the service provision of ANS in Hungary. <br/><br/>Operational: due to the closure of the Ukrainian airspace and the war-related sanctions, there have been reroutings in the Hungarian airspace, having a net positive impact on the number of overflights. <br/><br/>Traffic to and from Russia and Ukraine is missing, on the other hand, reroutings to and from North Europe, and the Far East (and other parts of Asia), as well as new routes between Russia and non-EU states have brought a significant amount of additional traffic. The size of this impact has further increased towards the year-end, as the traffic between Europe and Asia started to gain momentum. <br/><br/>The Hungarian ANSP experienced a very strong recovery (with overflights already passing the 2019-level (by 20% on some days) in 2022), and this was only in part a consequence of the reroutings, there was also a very strong increase of the organic traffic on the South-East axis. Especially in the summer, when leisure traffic from Western Europe to Greece and Türkiye created an unexpected high demand on our flow. <br/><br/>In addition to the already high demand, ANS provision was impacted by the war in one more way: there were military airspaces to decrease capacity and to increase complexity in the Hungarian airspace. <br/><br/>Reaction time: there is very little the Hungarian ANSP could have done to react to the explosion of traffic demand in the short run (i.e. through the course of 2022). ATCO training was postponed under COVID (as an adaptation to the traffic decrease) and although already resumed, cannot be accelerated on short notice. <br/><br/>The originally planned number of ATCOs was not (and will not be) enough to manage the traffic without disruptions (regulations, delays and re-routings of the re-routings).<br/><br/>The war has caused a significant increase in traffic in Budapest ACC, resulting in traffic reaching pre-COVID 2019 levels already in 2022. Budapest ACC was able to manage the unexpected traffic growth with ca. 60% fewer delays than in 2019, which was though not enough to meet the target, but allowed air traffic on the Eastern border of the Network to operate without any particular problems.<br/><br/>Our view is that had the war not broken out, Budapest ACC would have been able to handle the 2022 traffic within its capacity target.<br/><br/>We believe that a very significant part of the excess delay was due to the war. We have flagged this issue to the PRB and EC and also to the Network Management Board already, and although we understand that in 317/2019 the definition of "exceptional event" does not by word apply to our situation, we still believe that by the legislative intent a regular war in the neighbouring country, causing significant disruptions does qualify as an "exceptional event".

### Monitoring process for capacity performance
The war has caused a significant increase in traffic in Budapest ACC, resulting in traffic reaching pre-COVID 2019 levels already in 2022. <br/><br/>Budapest ACC was able to manage the unexpected traffic growth with ca 60% fewer delays than in 2019, which was though not enough to meet the target, but allowed air traffic on the Eastern border of the Network to operate without any particular problems.

### Capacity Planning
Capacity planning with NM for the year 2022 was completed in January with the conclusion that there will be no capacity issue.<br/><br/>Unfortunately at the end of February Russians started a war against Ukraine, and due to the closure of the Ukrainian airspace, all flights which have used that airspace for overflight before were forced to reroute via our airspace. <br/><br/>Unfortunately, the capacity planning process did not follow this huge rerouting and we were able to introduce only a few measures for summer in order to manage the extremely increased demand.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
The war has caused a significant increase in traffic in Budapest ACC, resulting in traffic reaching pre-COVID 2019 levels already in 2022. This was unexpected and the measures which were introduced during the first part of the year could only mitigate the capacity shortage. <br/><br/>Since there is no sign that the war in Ukraine will be over in 2023 and thus the traffic demand in Budapest ACC will remain very high, further adjustments are needed on terms of sector capacities and in the availability of ATCOs, through fine-tuning of the ATCO rostering.

### Summary of capacity performance
Hungary experienced an increase in traffic from 491k flights in 2021, with practically zero ATFM delays, to 897k flights in 2022 with 481k minutes of en route AFTM delay. <br/><br/>The traffic level in 2022 was higher than the 892k flights handled in 2019, which encountered treble the 2022 delays: 1.4 million minutes of ATFM delay. <br/><br/>There were an additional 318k minutes of en route ATFM delay originating in the Budapest ACC that were re-attributed to DFS (272k) and DSNA (46k) via the NM post operations delay attribution process, according to the NMB agreement for eNM/S22 measures, to ameliorate capacity shortfalls in both Karlsruhe UAC and Reims ACC.