[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
No specific capacity issues in 2022, actual traffic in (service units) was 1,1% above the level set in the Performance Plan. <br/><br/>The actual en-route ATFM delay per flight of 0,01 min./flt. was significant below the national target set to 0,08 min./flt. Actual performance is so far in RP3 much better than set in the revised Performance Plan.

### Monitoring process for capacity performance
Nothing reported

### Capacity Planning
Norway has been developing ATC capacity over years, and is in position to provide more capacity than the national reference values.The cost optimum capacity for en route delay per flight for Avinor ANS is between 0,18 min/flt. and 0,11 min/flt., but for the airspace users this would be unacceptable. <br/><br/>This view is based on the fact that a large portion of the overall traffic is transition flights with little leeway in terms of delays. Based on consultation meetings with the airspace users and Avinor ANS during the en route delay is set to between 0,08 min./flt and 0,11 min./flt. in RP3.<br/><br/>Avinor ANS has over the last years been increasing capacity, in order to being able to shift to new technology without major operational consequences for the airspace users.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
Initial drop in overflights estimated to around 20%. Some of the traffic have recovered since the initial phase. In general en route capacity has not been affected.<br/>

### Summary of capacity performance
Norway experienced an increase in traffic from 376k flights in 2021, with zero ATFM delay, to 529k flights in 2022 - with marginal delay (3k minutes).<br/><br/>Traffic levels were still below the 595k flights in 2019.