```{r cef-level2-text}
cz=c("@@cz_index@@", "@@cz_type@@")
  
# define cz
ez <- as.numeric(cz[[1]])
cztype <- cz[[2]]

if (country == "SES RP3") {
  # to avoid errors when processing the file
  cef_txt_1_4_duc <- ''
  cef_txt_1_4_su <- '' 
  cef_txt_1_4_cost_all <- ''
  cef_txt_1_4_cost_main <- ''
  cef_txt_1_4 <- data.frame(a=c(NA,NA), b=c(NA,NA)) |> as_tibble()
  
  my_index_su <- 1
  my_index_cost_by_ent <- 1
  my_index_cost_main <- 1
  
  cef_txt_1_5 <- data.frame(a=c(NA,NA), b=c(NA,NA)) |> as_tibble()
  cef_txt_1_10 <- data.frame(a=c(NA,NA), b=c(NA,NA)) |> as_tibble()
  cef_txt_1_13 <- data.frame(a=c(NA,NA,NA,NA,NA), b=c(NA,NA,NA,NA,NA)) |> as_tibble()
  
} else {
  # define ranges and import data
  ## 1st sheet
  sheet <- if_else(cztype == "terminal",
                   if_else(ez >1, paste0("5_TRM (", ez, ")"), "5_TRM"),
                   "1_ERT")
  ceff_file <- if_else(country == "Spain" & ez == 2, ceff_file_canarias, ceff_file)
  
  ## range 1.4
  range <- "C50:M71"
  cef_txt_1_4  <- read_range(ceff_file, sheet, range) %>% rename(a = 1)
  
  ### Check if the whole range is merged and apply different logic
  if (is.na(cef_txt_1_4[2,1]) == FALSE) {
    ### find specific headings
    my_index_su <- which(cef_txt_1_4$a %like% paste0(if_else(cztype == "terminal",
                                                             "Terminal",
                                                             "En route"), 
                                                     ' service units')) + 1
    
    if(identical(my_index_su, numeric(0)) == TRUE) {my_index_su <- which(cef_txt_1_4$a %like% paste0("Terminal charging zone ", ez,' service units')) + 1} 
    
    my_index_cost_by_ent <- which(cef_txt_1_4$a %like% paste0(if_else(cztype == "terminal",
                                                             "Terminal",
                                                             "En route"), 
                                                     ' costs by entity')) + 1
    
    if(identical(my_index_cost_by_ent, numeric(0)) == TRUE) {my_index_cost_by_ent <- which(cef_txt_1_4$a %like% paste0("Terminal charging zone ", ez,' costs by entity')) + 1} 
    
    my_index_cost_main <- which(cef_txt_1_4$a %like% paste0(if_else(cztype == "terminal",
                                                             "Terminal",
                                                             "En route"), 
                                                     " costs for the main ANSP")) + 1
    
    if(identical(my_index_cost_main, numeric(0)) == TRUE) {my_index_cost_main <- which(cef_txt_1_4$a %like% paste0("Terminal charging zone ", ez,' costs for the main ANSP')) + 1}
    if(identical(my_index_cost_main, numeric(0)) == TRUE) {my_index_cost_main <- which(cef_txt_1_4$a %like% paste0("Terminal charging zone costs for the main ANSP")) + 1}
    
    ### to avoid errors if else is executed
    cef_txt_1_4_duc <- ""
    cef_txt_1_4_su <- ""
    cef_txt_1_4_cost_all <- ""
    cef_txt_1_4_cost_main <- ""
  
  } else {
    ### find beginning and end of headings
    tx <- cef_txt_1_4[1,1] |> pull()
    heading1 <- str_locate(tx, fixed('AUC vs DUC')) + 7 
    if(is.na(heading1[1]) == TRUE) {heading1 <- str_locate(tx, fixed('AUC vs. DUC')) + 7}
    heading2 <- str_locate(tx, fixed(paste0(if_else(cztype == "terminal",
                                                             "**Terminal",
                                                             "**En route"), 
                                                     " service units"))) 
  
    heading3_1 <- str_locate(tx, fixed(paste0(if_else(cztype == "terminal",
                                                             "**Terminal",
                                                             "**En route"),
                                              ' costs by entity at charging zone level**<br/>')))
    heading3_2 <- str_locate(tx, fixed(paste0(if_else(cztype == "terminal",
                                                             "**Terminal",
                                                             "**En route"),
                                              ' costs by entity**<br/>')))
  
    heading4_beg <- str_locate(tx, fixed(paste0(if_else(cztype == "terminal",
                                                             "**Terminal",
                                                             "**En route"),
                                              ' costs for the main ANSP')))
    all_bold_locations <- str_locate_all(tx, fixed('**'))
    heading_4 <- tail(all_bold_locations[[1]], n = 1)
  
    cef_txt_1_4_duc <- str_replace_all(substr(tx, max(heading1)+1, min(heading2)-1), fixed("<br/><br/>"), fixed("<br/>"))
    cef_txt_1_4_su <- str_replace_all(substr(tx, max(heading2)+1+7, min(heading3_1, heading3_2, na.rm = TRUE)-1) , fixed("<br/><br/>"), fixed("<br/>"))
    cef_txt_1_4_cost_all <- str_replace_all(substr(tx, max(heading3_1, heading3_2, na.rm = TRUE)+1, min(heading4_beg)-1) , fixed("<br/><br/>"), fixed("<br/>"))
    cef_txt_1_4_cost_main <- str_replace_all(substr(tx, heading_4 + 2, nchar(tx)) , fixed("<br/><br/>"), fixed("<br/>"))
    
    ### remove leading and trailing line breaks
    cef_txt_1_4_duc <- sub("^<br/>|<br/>$", "", cef_txt_1_4_duc)
    cef_txt_1_4_su <- sub("^<br/>|<br/>$", "", cef_txt_1_4_su)
    cef_txt_1_4_cost_all <- sub("^<br/>|<br/>$", "", cef_txt_1_4_cost_all)
    cef_txt_1_4_cost_main <- sub("^<br/>|<br/>$", "", cef_txt_1_4_cost_main)
    
    ### just to avoid errors
    my_index_su <- 2
    my_index_cost_by_ent <-2
    my_index_cost_main <- 2
  
    }
    
  ## 2nd sheet
  sheet <- if_else(cztype == "terminal",
                   if_else(ez >1, paste0("6_TRM (", ez, ")"), "6_TRM"),
                   "2_ERT")
  range <- "C11:M14"
  cef_txt_1_5  <- read_range(ceff_file, sheet, range)
  
  range <- "J16:M33"
  cef_txt_1_6  <- read_range(ceff_file, sheet, range)
  
  ## range 1.9
  range <- "C63:M70"
  cef_txt_1_9  <- read_range(ceff_file, sheet, range)
  
  ## 3rd sheet
  sheet <- if_else(cztype == "terminal",
                   if_else(ez >1, paste0("7_TRM_ATSP (", ez, ")"), "7_TRM_ATSP"),
                   "3_ATSP")
  
  range <- "C11:M22"
  cef_txt_1_10  <- read_range(ceff_file, sheet, range)
  
  range <- if_else(year_report >= 2022, "C66:M71", "C64:M71")
  cef_txt_1_13  <- read_range(ceff_file, sheet, range)
  ## the titles are already bold in the .qmd below
  if (year_report >= 2023) {
    cef_txt_1_13 <- cef_txt_1_13 %>% 
      mutate_all(., ~ str_replace_all(., fixed("**"),""))
  }
}
```

[Cost-efficiency - {{< var doc.country >}}]{class="fakeh1"}


`r if (cztype == 'terminal' | ez == 2) "::: {.content-hidden}"`

::: {#container-cef-prb}
## PRB assessment

:::: {#concl-cef-duc}
```{r concl-cef-duc}
cef_conc <- read_mytable("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF") %>%
  filter(Year_Report == params$year_report, State == params$country) %>%
  select(Conclusion) %>% toString() %>% paste0(., "@")

cef_conc1 <- cef_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n')
```

`r cef_conc1`

::::
:::
`r if (cztype == 'terminal' | ez == 2) ":::"`


`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## @@cz_type_proper@@ Charging Zone - {{< var doc.@@cz_short@@@@cz_index@@ >}}
`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) ":::"`


`r if ((params$no_ecz != 1 & cztype == 'enroute') | (params$no_tcz >= 2 & cztype == 'terminal')) "::: {.content-hidden}"`
## @@cz_type_proper@@ Charging Zone
`r if ((params$no_ecz != 1 & cztype == 'enroute') | (params$no_tcz >= 2 & cztype == 'terminal')) ":::"`

::: {#container-cef-duc}

### Unit cost (KPI#1)

:::: {layout="[ 50, 50 ]"}

::::: {#chart-cef-duc}
`r if (params$country == "SES RP3" & cztype == "enroute") ":::::: {.content-hidden}"`
```{r chart-cef-duc, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```
`r if (params$country == "SES RP3" & cztype == "enroute") "::::::"`

`r if (params$country != "SES RP3" | cztype == "terminal") ":::::: {.content-hidden}"`
```{r chart-cef-duc-er-ses, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```
`r if (params$country != "SES RP3" | cztype == "terminal") "::::::"`

:::::

::::: {#chart-cef-su}
```{r chart-cef-su, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-cost}
```{r chart-cef-cost, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```
:::::

::::: {#table-costs}
```{r table-cef-cost, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cost.R
#| out.width: "100%"
```

`r if (params$country == "SES RP3") ":::::: {.content-hidden}"`

```{r table-cef-cost-infl, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cost_infl.R
#| out.width: "100%"
```
`r if (params$country == "SES RP3") "::::::"`
:::::
::::


:::: {layout="[ 50, 50 ]"}

::::: {#chart-cef-cost-entity}
```{r chart-cef-cost-entity, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost_entity.R
#| out.width: "100%"
```
:::::

::::: {#chart-cef-cost-main class="mychart"}
```{r chart-cef-cost-main, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost_main.R
#| out.width: "100%"
```
:::::
::::
:::

`r if (params$country == "SES RP3") "::: {.content-hidden}"`
::: {.callout-note collapse=true}

#### NSA input

**AUC vs. DUC**

`r if_else(is.na(cef_txt_1_4[2,1]) == TRUE, cef_txt_1_4_duc, pull(cef_txt_1_4[2,1]))`

**En route service units**

`r if_else(is.na(cef_txt_1_4[my_index_su,1]) == TRUE, cef_txt_1_4_su, pull(cef_txt_1_4[my_index_su,1]))`

**En route costs by entity**

`r if_else(is.na(cef_txt_1_4[my_index_cost_by_ent,1]) == TRUE, cef_txt_1_4_cost_all, pull(cef_txt_1_4[my_index_cost_by_ent,1]))`

**En route costs for the main ANSP at charging zone level**

`r if_else(is.na(cef_txt_1_4[my_index_cost_main,1]) == TRUE, cef_txt_1_4_cost_main, pull(cef_txt_1_4[my_index_cost_main,1]))`

:::
`r if (params$country == "SES RP3") ":::"`


::: {#container-cef-aucu}

### AUCU (PI#1)

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-aucu}
```{r chart-cef-aucu, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```
:::::

::::: {#table-cef-aucu}
```{r table-cef-aucu, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_aucu.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}

::::: {#chart-cef-er-cex}
```{r chart-cef-cex, R.options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```
:::::

::::: {#table-cef-er-cex}
```{r table-cef-cex, R.options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cex.R
#| out.width: "100%"
```
:::::
::::
:::

`r if (params$country == "SES RP3") "::: {.content-hidden}"`
::: {.callout-note collapse=true}

#### NSA input

`r cef_txt_1_5[1,1]`

:::
`r if (params$country == "SES RP3") ":::"`


::: {#container-cef-reg-res}

### Regulatory result

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-reg-res}
```{r chart-cef-reg-res, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```
:::::

::::: {#chart-cef-reg-res-aucu}
```{r chart-cef-reg-res_aucu,  options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-reg-res-ansp}
```{r chart-cef-reg-res-ansp, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```
:::::

::::: {#chart-cef-reg-res-main-ansp}
```{r chart-cef-net-res-main-ansp, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```
:::::
::::

:::

`r if (params$country == "SES RP3") "::: {.content-hidden}"`
::: {.callout-note collapse=true}

#### NSA input

**Monitoring of the en route ANSPs regulatory results (RR)**

`r cef_txt_1_10[1,1]`

`r if (params$year_report < 2022) "::: {.content-hidden}"`

**`r cef_txt_1_13[1,1]`**

`r cef_txt_1_13[2,1]`

**`r cef_txt_1_13[3,1]`**

`r cef_txt_1_13[4,1]`

`r if (params$year_report < 2022) ":::"`

`r if (params$year_report >= 2022) "::: {.content-hidden}"`

`r cef_txt_1_13[1,1]`

`r if (params$year_report >= 2022) ":::"`

:::
`r if (params$country == "SES RP3") ":::"`

