```{r env-level2-text}
# define ranges and import data
sheet <- country

if (no_tcz >0) {
range <- "A2:P80"
env_apt_all <- read_range(env_apt_file, sheet, range) 
env_apt_all <- env_apt_all |> 
    rename(a = 1) 

# replace NAs by empty strings
env_apt_all[is.na(env_apt_all)] <- ""

env_apt_titles <- c("1. Overview",
                "**1. Overview**",
                "2. Additional Taxi-Out Time", 
                "**2. Additional Taxi-Out Time**", 
                "3. Additional ASMA Time",
                "**3. Additional ASMA Time**",
                "4. Share of arrivals applying CDO",
                "**4. Share of arrivals applying CDO**",
                "5. Appendix",
                "**5. Appendix**"
)

env_apt_heading_positions <- which(env_apt_all$a %in% env_apt_titles)

for (i in 1:length(env_apt_heading_positions)) {
  if (i<length(env_apt_heading_positions)) {
    mytext <- apply(env_apt_all[(env_apt_heading_positions[i]+1):(env_apt_heading_positions[i+1]-1), ], 1, function(col) paste(col, collapse = "<br>"))
  } else{
    mytext <- apply(env_apt_all[(env_apt_heading_positions[i]+1):(env_apt_heading_positions[i]+1), ], 1, function(col) paste(col, collapse = "<br>"))

  }
  # replace repeated breaks by single  
  mytext <- gsub("(<br>)+", "<br>", mytext)

  #remove empty elements of vector
  mytext <- mytext[mytext != "<br>"]
  mytext <- mytext[mytext != ""]
  
  #replace double breaks by single breaks
  pattern <- "(<br>){2,}"
  mytext <- str_replace_all(mytext, pattern, "<br>")

  ### remove leading and trailing line breaks
  mytext <- sub("^<br>|<br>$", "", mytext)
  
  ### assign text to variable
  assign(paste0("env_apt_", i, "_r"), mytext)
}


# # env apt old code based on ranges
# range <- "A3:P4"
# env_apt_1_r <- read_range(env_apt_file, sheet, range)  
# 
# range <- "A5:P7"
# env_apt_2_r <- read_range(env_apt_file, sheet, range) 
# env_apt_2_r <- if_else(is.na(env_apt_2_r[2,1]) == FALSE, pull(env_apt_2_r[2,1]), pull(env_apt_2_r[1,8]))
# 
# range <- "A8:P10"
# env_apt_3_r <- read_range(env_apt_file, sheet, range) 
# env_apt_3_r <- if_else(is.na(env_apt_3_r[2,1]) == FALSE, pull(env_apt_3_r[2,1]), pull(env_apt_3_r[1,8]))
# 
# range <- "A11:P13"
# env_apt_4_r <- read_range(env_apt_file, sheet, range) 
# env_apt_4_r <- if_else(is.na(env_apt_4_r[2,1]) == FALSE, pull(env_apt_4_r[2,1]), pull(env_apt_4_r[1,8])) 
# 
# range <- "A14:P15"
# env_apt_5_r <- read_range(env_apt_file, sheet, range)   
}

# env mil
range <- "A2:P80"
env_mil_all <- read_range(env_mil_file, sheet, range) 
env_mil_all <- env_mil_all |> 
    rename(a = 1) 

# replace NAs by empty strings
env_mil_all[is.na(env_mil_all)] <- ""

env_mil_titles <- c("Update on Military dimension of the plan",
                "**Update on Military dimension of the plan**",
                "Military - related measures implemented or planned to improve capacity", 
                "**Military - related measures implemented or planned to improve capacity**",
                "PI#6 Effective use of reserved or segregated airspace - national level",
                "**PI#6 Effective use of reserved or segregated airspace - national level**",
                "Initiatives implemented or planned to improve PI#6",
                "**Initiatives implemented or planned to improve PI#6**",
                "**PI#7 Rate of planning via available airspace structures - national level**",
                "PI#7 Rate of planning via available airspace structures - national level**",
                "Initiatives implemented or planned to improve PI#7",
                "**Initiatives implemented or planned to improve PI#7**",
                "PI#8 Rate of using available airspace structures - national level",
                "**PI#8 Rate of using available airspace structures - national level**",
                "Initiatives implemented or planned to improve PI#8",
                "**Initiatives implemented or planned to improve PI#8**"
)

env_mil_heading_positions <- which(env_mil_all$a %in% env_mil_titles)

for (i in 1:length(env_mil_heading_positions)) {
  if (i<length(env_mil_heading_positions)) {
    mytext <- apply(env_mil_all[(env_mil_heading_positions[i]+1):(env_mil_heading_positions[i+1]-1), ], 1, function(col) paste(col, collapse = "<br>"))
  } else{
    mytext <- apply(env_mil_all[(env_mil_heading_positions[i]+1):(env_mil_heading_positions[i]+4), ], 1, function(col) paste(col, collapse = "<br>"))

  }
  # replace repeated breaks by single  
  mytext <- gsub("(<br>)+", "<br>", mytext)

  #remove empty elements of vector
  mytext <- mytext[mytext != "<br>"]
  mytext <- mytext[mytext != ""]
  
  #replace double breaks by single breaks
  pattern <- "(<br>){2,}"
  mytext <- str_replace_all(mytext, pattern, "<br>")

  ### remove leading and trailing line breaks
  mytext <- sub("^<br>|<br>$", "", mytext)
  
  ### assign text to variable
  assign(paste0("env_mil_", i, "_r"), mytext)
}

# 
# range <- "A3:O7"
# env_mil_3_r <- read_range(env_mil_file, sheet, range) 
# 
# range <- "A8:O12"
# env_mil_2_r <- read_range(env_mil_file, sheet, range) 
# 
# range <- "A30:O34"
# env_mil_5_r <- read_range(env_mil_file, sheet, range) 
# 
# range <- "A52:O56"
# env_mil_8_r <- read_range(env_mil_file, sheet, range) 
# 
# range <- "A74:O78"
# env_mil_11_r <- read_range(env_mil_file, sheet, range) 

```

[Environment - {{< var doc.country >}}]{class="fakeh1"}

::: {#container-env-prb}

## PRB assessment
:::: {#concl-kea}
```{r}
env_conc <- read_mytable("PRB_findings.xlsx", "environment", "Table_Findings_environment") %>%
  filter(Year_Report == params$year_report, State == params$country) %>%
  select(Conclusion) %>% toString() %>% paste0(., "@")

env_conc1 <- env_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n')
```

`r env_conc1`
::::

:::

::: {#container-kea}

## En route performance

### Horizontal flight efficiency

:::: {layout="[ 50, 50 ]"}

::::: {#chart-env-kea}

```{r chart-env-kea}
#| file: R/chart_level1_kea.R
#| out.width: "50%"
```

:::::

::::: {#chart-env-kea-month}

```{r chart-env-kea-month}
#| file: R/chart_level2_kea_month.R
#| out.width: "50%"
```

:::::

::::

:::: {layout="[ 50, 50 ]"}

::::: {#chart-kep-scr}
```{r chart-env-kep-scr}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

:::::

::::: {#chart-kep-scr-month}

```{r chart-env-kep-scr-month}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```
:::::

::::
:::

`r if (params$no_tcz == 0) "::: {.content-hidden}"`

::: {#container-axot-asma}

## Terminal performance

### AXOT & ASMA

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {#chart-axot-asma}
```{r chart-axot-asma-country}
#| file: R/chart_level2_env_axot_asma_country.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}

::::: {#chart-axot}
```{r chart-axot-apt}
#| file: R/chart_level2_env_axot_apt.R
#| out.width: "100%"
```
:::::

::::: {#chart-asma}
```{r chart-asma-apt}
#| file: R/chart_level2_env_asma_apt.R
#| out.width: "100%"
```
:::::

::::
:::

::: {.callout-note collapse=true}

#### NSA input

**AXOT**

`r if (exists("env_apt_2_r") == FALSE) {''} else {env_apt_2_r}`

**ASMA**

`r if (exists("env_apt_3_r") == FALSE) {''} else {env_apt_3_r}`

:::

::: {#container-cdo}

### CDO

:::: {layout="[ 50, 50 ]"}

::::: {#chart-cdo-country}
```{r chart-cdo-country}
#| file: R/chart_level2_env_cdo_country.R
#| out.width: "100%"
```
:::::

::::: {#chart-cdo-apt}
```{r chart-cdo-apt}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "100%"
```
:::::

::::
:::

::: {.callout-note collapse=true}

#### NSA input

`r if (exists("env_apt_4_r") == FALSE) {''} else {env_apt_4_r}`

:::

::: {#container-env-apt-pis}

:::: {#table-env-apt-pis}

```{r table-env-apt-pis}
#| file: R/table_level2_env_apt_pis.R
#| out.width: "100%"
```

::::
:::

`r if (params$no_tcz == 0) ":::"`

::: {#container-mil-pi}

## Civil-Military dimension 

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {#chart-ersa}
```{r chart-ersa}
#| file: R/chart_level2_env_ersa.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}

::::: {#chart-cdr}
```{r chart-cdr}
#| file: R/chart_level2_env_cdr.R
#| out.width: "100%"
```
:::::

::::: {#chart-rsa}
```{r chart-rsa}
#| file: R/chart_level2_env_rsa.R
#| out.width: "100%"
```
:::::

::::
:::

::: {.callout-note collapse=true}

#### NSA input

**Update on Military dimension of the plan**

`r env_mil_1_r`

**Military - related measures implemented or planned to improve capacity**

`r env_mil_2_r`

**Initiatives implemented or planned to improve PI#6**

`r env_mil_4_r`

**Initiatives implemented or planned to improve PI#7**

`r env_mil_6_r`

**Initiatives implemented or planned to improve PI#8**

`r env_mil_8_r`

:::
