##  Military dimension
### Update on Military dimension of the plan

LARA has been implemented and Civil/Military Airspace Committee maintain a continued focus on the effectiveness of the booking procedures.<br/><br/>The AMC procedure has been revised establishing new and larger areas in southern Norway with a design that is optimized to cater to civilian traffic flows. The civil/military airspace continually work on optimizing the airspace structure to minimize the impact of military air operations on civilian air traffic. LARA has been deployed to both civil and military users and further integration into the ATM system is ongoing.

### Military - related measures implemented or planned to improve capacity

The AMC procedure has been revised establishing new and larger areas in southern Norway with a design that is optimized to cater to civilian traffic flows. The Civil/military airspace committee focus on the improvement of the booking procedures and the intention to improve the ratio between booked versus used reserved airspace.<br/><br/>The civil/military airspace continually work on optimizing the airspace structure to minimize the impact of military air operations on civilian air traffic. LARA has been deployed to both civil and military users and further integration into the ATM system is ongoing.

### PI#6 Effective use of reserved or segregated airspace - national level

```{r,  options=(range = "B15:N17")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r,  options=(range = "B20:N29")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

No data available per ACC

### PI#7 Rate of planning via available airspace structures - national level

```{r,  options=(range = "B37:N39")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r,  options=(range = "B42:N51")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

No data available per ACC

### PI#8 Rate of using available airspace structures - national level

```{r,  options=(range = "B59:N61")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r,  options=(range = "B64:N73")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

No data available per ACC