```{r cap-level2-text}
# define ranges and import data
sheet <- country

# env apt 
range <- "A3:P4"
env_apt_1_r <- read_range(env_apt_file, sheet, range)  

range <- "A5:P7"
env_apt_2_r <- read_range(env_apt_file, sheet, range) 
env_apt_2_r <- if_else(is.na(env_apt_2_r[2,1]) == FALSE, pull(env_apt_2_r[2,1]), pull(env_apt_2_r[1,8]))

range <- "A8:P10"
env_apt_3_r <- read_range(env_apt_file, sheet, range) 
env_apt_3_r <- if_else(is.na(env_apt_3_r[2,1]) == FALSE, pull(env_apt_3_r[2,1]), pull(env_apt_3_r[1,8]))

range <- "A11:P13"
env_apt_4_r <- read_range(env_apt_file, sheet, range) 
env_apt_4_r <- if_else(is.na(env_apt_4_r[2,1]) == FALSE, pull(env_apt_4_r[2,1]), pull(env_apt_4_r[1,8])) 

range <- "A14:P15"
env_apt_5_r <- read_range(env_apt_file, sheet, range)   

# env mil

range <- "A3:O7"
env_mil_1_r <- read_range(env_mil_file, sheet, range) 

range <- "A8:O12"
env_mil_2_r <- read_range(env_mil_file, sheet, range) 

range <- "A30:O34"
env_mil_5_r <- read_range(env_mil_file, sheet, range) 

range <- "A52:O56"
env_mil_8_r <- read_range(env_mil_file, sheet, range) 

range <- "A74:O78"
env_mil_11_r <- read_range(env_mil_file, sheet, range) 

```

[2 Environment - {{< var doc.country >}}]{class="fakeh1"}

::: {#container-kea style="clear: both"}

## KPI - KEA

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

:::: {#chart-kea class="mychart"}
```{r chart-env-kea}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart-env-kea-month}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```
::::

:::: {#concl-kea}
```{r}
env_conc <- read_mytable("PRB_findings.xlsx", "environment", "Table_Findings_environment") %>%
  filter(Year_Report == params$year_report, State == params$country) %>%
  select(Conclusion) %>% toString() %>% paste0(., "@")

env_conc1 <- env_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n')
```

`r env_conc1`
::::
:::

::: {#container-kep-scr style="clear: both"}

## PIs - KEP and SCR

<!-- empty line to ensure next heading leaves enough space -->
<!-- <div style="height: 1px"></div> -->

:::: {#chart-kep-scr class="mychart"}
```{r chart-env-kep-scr}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart-env-kep-scr-month}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```
::::

:::: {#concl-kep-scr}

::::
:::

`r if (params$no_tcz == 0) "::: {.content-hidden}"`

::: {#container-axot-asma style="clear: both"}

## PIs - AXOT and ASMA

<!-- empty line to ensure next heading leaves enough space -->
<!-- <div style="height: 1px"></div> -->

:::: {#chart-axot-asma class="mychart"}
```{r chart-axot-asma-country}
#| file: R/chart_level2_env_axot_asma_country.R
#| out.width: "100%"
```

::::

:::: {#concl-axot-asma}
`r env_apt_1_r[1,1]`
::::
:::

::: {#container-axot style="clear: both"}

:::: {#chart-axot class="mychart"}
```{r chart-axot-apt}
#| file: R/chart_level2_env_axot_apt.R
#| out.width: "100%"
```
::::

:::: {#concl-axot}
`r env_apt_2_r`
::::
:::

::: {#container-axot style="clear: both"}

:::: {#chart-asma class="mychart"}
```{r chart-asma-apt}
#| file: R/chart_level2_env_asma_apt.R
#| out.width: "100%"
```
::::

:::: {#concl-asma}
`r env_apt_3_r`
::::
:::


::: {#container-cdo style="clear: both"}

## PIs - CDO

:::: {#chart-cdo class="mychart"}
```{r chart-cdo-country}
#| file: R/chart_level2_env_cdo_country.R
#| out.width: "100%"
```

```{r chart-cdo-apt}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "100%"
```
::::

:::: {#concl-cdo}

`r env_apt_4_r`

::::
:::

::: {#container-env-apt-pis style="clear: both"}

`r env_apt_5_r[1,1]`

:::: {#table-env-apt-pis}

```{r table-env-apt-pis}
#| file: R/table_level2_env_apt_pis.R
#| out.width: "100%"
```

::::
:::

`r if (params$no_tcz == 0) ":::"`

::: {#container-mil-pi style="clear: both"}

## Military PIs

:::: {#table-env-mil-pi class="mychart"}
```{r table-env-mil-pi}
#| file: R/table_level2_env_mil_pi.R
#| out.width: "100%"
```
::::

:::: {#concl-mil-pi}

**Update on Military dimension of the plan**

`r env_mil_1_r[1,1]`

**Military - related measures implemented or planned to improve capacity**

`r env_mil_2_r[1,1]`

**Initiatives implemented or planned to improve PI#6**

`r env_mil_5_r[1,1]`

**Initiatives implemented or planned to improve PI#7**

`r env_mil_8_r[1,1]`

**Initiatives implemented or planned to improve PI#8**

`r env_mil_11_r[1,1]`

::::
:::