[Investments - {{< var doc.country >}}]{.fakeh1}

## PRB monitoring
[Placeholder for text]												

## Value of the assets for New Investments included in the Performance Plan `r country` | `r main_ansp`

### Determined and additional asset value by investment category

::: {layout="[ 62, 0, 38 ]"}
:::: {#table_invest_av_type}
```{r table_invest_av_type}
#| file: R/table_invest_av_type.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_av_type}
```{r chart_invest_av_type}
#| file: R/chart_invest_av_type.R
#| out.width: "100%"
```
::::
:::

### Determined asset value: en route and terminal

::: {layout="[ 62, 0, 38 ]"}
:::: {#table_invest_av_er_trm}
```{r table_invest_av_er_trm}
#| file: R/table_invest_av_er_trm.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_av_er_trm}
```{r chart_invest_av_er_trm}
#| file: R/chart_invest_av_er_trm.R
#| out.width: "100%"
```
::::
:::

### Determined asset value by type of investment

::: {layout="[ 62, 0, 38 ]"}
:::: {#table_invest_av_category}
```{r table_invest_av_category}
#| file: R/table_invest_av_category.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_av_category}
```{r chart_invest_av_category}
#| file: R/chart_invest_av_category.R
#| out.width: "100%"
```
::::
:::

### Asset value for new investments: ANSP compared to Union-wide

::: {layout="[ 33, 33, 33 ]"}
:::: {#chart_invest_av_vs_eu1}
```{r chart_invest_av_vs_eu1}
#| file: R/chart_invest_av_vs_eu1.R
#| out.width: "100%"
```
::::

::::{#chart_invest_av_vs_eu2}
```{r chart_invest_av_vs_eu2}
#| file: R/chart_invest_av_vs_eu2.R
#| out.width: "100%"
```
::::

:::: {#chart_invest_av_vs_eu3}
```{r chart_invest_av_vs_eu3}
#| file: R/chart_invest_av_vs_eu3.R
#| out.width: "100%"
```
::::
:::


## Costs related to investments included in the Performance Plan `r country` | `r main_ansp`

### New and existing investments 

```{r}
#| label: table_invest_cost_total
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_total.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {#chart_invest_cost_total}
```{r chart_invest_cost_total}
#| file: R/chart_invest_cost_total.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_cost_category}
```{r chart_invest_cost_category}
#| file: R/chart_invest_cost_category.R
#| out.width: "100%"
```
::::
:::

### Costs of investments by nature - En route

```{r, options= (cost_type = "en route")}
#| label: table_invest_cost_nature_er
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_nature.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>


::: {layout="[10, 80, 10]"}
:::: {#empty_div}
::::

::::{#empty_div}
```{r chart_invest_difference_cost_er, options= (cost_type = "en route")}
#| file: R/chart_invest_difference_cost.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::

`r if (params$no_tcz == 0) "::: {.content-hidden}"`

### Costs of investments by nature - Terminal

```{r, eval=(params$no_tcz != 0), options= (cost_type = "terminal")}
#| label: table_invest_cost_nature_trm
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_nature.R")
table1
```

```{r, eval=(params$no_tcz != 0)}
#| echo: false
table2
```

```{r, eval=(params$no_tcz != 0)}
#| echo: false
table3
```

<br>


::: {layout="[10, 80, 10]"}
:::: {#empty_div}
::::

::::{#empty_div}
```{r chart_invest_difference_cost_trm, eval=(params$no_tcz != 0), options= (cost_type = "terminal")}
#| file: R/chart_invest_difference_cost.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::

`r if (params$no_tcz == 0) ":::"`

### Costs by new major investments

```{r}
#| label: table_invest_cost_new_major
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_new_major.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>

```{r no_investment, include=FALSE}
source("R/chart_invest_cost_new_major.R")
no_investments <- no_investments
```

`r if (no_investments <= 6)"::: {.content-hidden}"`
```{r chart_invest_cost_new_major_many, eval=(no_investments > 6)}
#| file: R/chart_invest_cost_new_major.R
#| out.width: "100%"
```
`r if (no_investments <= 6)":::"`



`r if (no_investments > 6)"::: {.content-hidden}"`
::: {layout="[ 10, 80, 10 ]"}
:::: {#empty_div}
::::

::::{#chart_invest_cost_new_major}
```{r chart_invest_cost_new_major_few, eval=(no_investments <= 6)}
#| file: R/chart_invest_cost_new_major.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::
`r if (no_investments > 6)":::"`

## Expected benefit and impact per new major investment `r country` | `r main_ansp`

```{r table_invest_benefits_kpa}
#| file: R/table_invest_benefits_kpa.R
#| out.width: "100%"
```

```{r table_invest_benefits}
#| file: R/table_invest_benefits.R
#| out.width: "100%"
```

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {#chart_invest_benefits_kpa}
```{r chart_invest_benefits_kpa}
#| file: R/chart_invest_benefits_kpa.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_benefits}
```{r chart_invest_benefits}
#| file: R/chart_invest_benefits.R
#| out.width: "100%"
```
::::
:::


```{r table_invest_type}
#| file: R/table_invest_type.R
#| out.width: "100%"
```

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {#chart_invest_type_eu}
```{r chart_invest_type_eu}
#| file: R/chart_invest_type_eu.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_type}
```{r chart_invest_type}
#| file: R/chart_invest_type.R
#| out.width: "100%"
```
::::
:::


## Public funding granted for total CAPEX (CEF/TEN-T) 

### Actual funding declaration vs payments

```{r table_invest_funding}
#| file: R/table_invest_funding.R
#| out.width: "100%"
```

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {#chart_invest_funding_year}
```{r chart_invest_funding_year}
#| file: R/chart_invest_funding_year.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {#chart_invest_funding_vs_eu}
```{r chart_invest_funding_vs_eu}
#| file: R/chart_invest_funding_vs_eu.R
#| out.width: "100%"
```
::::
:::