```{r saf-level2-text}
# define ranges and import data
if (params$country == "SES RP3") {
  saf_text <- ""
  
} else {
  sheet <- country
  
  range <- "A15:G30"
  saf_all <- read_range(saf_eosm_file, sheet, range) 
  saf_all <- saf_all |> 
      rename(a = 1) 
  
  # replace NAs by empty strings
  saf_all[is.na(saf_all)] <- ""
  
  #define titles to lookup
  saf_titles <- c("Observations",
                  "**Observations**"
  )
  
  saf_heading_positions <- which(saf_all$a %in% saf_titles)
  
  saf_text <- saf_all[(saf_heading_positions[1]+1):(saf_heading_positions[1]+1), 1]
}

```
::: {.grid .align-items-center}
:::: {.g-col-9}
[Safety - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}
</span>
::::
:::


## PRB monitoring
```{r concl-saf}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

::: {#container-saf-indicators}

`r if_else(params$country == "SES RP3", "## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024", "## Effectiveness of Safety Management (EoSM) (KPI#1)")`

```{r, eval = params$country != "SES RP3"}
#| label: chart_saf_eosm
#| out.width: "100%"
#| echo: false

source("R/chart_level1_saf.R")
```

`r if (params$country != "SES RP3" & params$no_saf_ansps >1) ":::: {.content-hidden}"`

::::: {layout="[ 20, 60, 20 ]"}

:::::: {#empty-div}
::::::

:::::: {.chart-container}  
`r if (params$country != "SES RP3") ":::::: {.content-hidden}"`
```{r chart_saf_ansp_ses, eval = params$country == "SES RP3"}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```
`r if (params$country != "SES RP3") "::::::"`

`r if (params$country == "SES RP3") ":::::: {.content-hidden}"`
```{r, eval = params$country != "SES RP3"}
#| echo: false
mycharts[[1]]
```
`r if (params$country == "SES RP3") "::::::"`
::::::
:::::
`r if (params$country != "SES RP3" & params$no_saf_ansps >1) "::::"`


`r if (params$country == "SES RP3" | params$no_saf_ansps == 1) ":::: {.content-hidden}"`
::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r, eval = params$country != "SES RP3"}
#| echo: false
mycharts[[1]]
```
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != "SES RP3") & (params$no_saf_ansps > 1)}
#| echo: false
mycharts[[2]]
```
:::::: 
:::::
`r if (params$country == "SES RP3" | params$no_saf_ansps == 1) "::::"`


`r if (params$country == "SES RP3" | params$no_saf_ansps != 3) ":::: {.content-hidden}"`
::::: {layout="[ 25, 50, 25 ]"}

:::::: {#emptydiv}  
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != "SES RP3") & (params$no_saf_ansps > 2)}
#| echo: false
mycharts[[3]]
```
:::::: 

:::::: {#emptydiv}  
:::::: 
:::::
`r if (params$country == "SES RP3" | params$no_saf_ansps != 3) "::::"`


`r if (params$country == "SES RP3" | params$no_saf_ansps != 4) ":::: {.content-hidden}"`
::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r, eval = (params$country != "SES RP3") & (params$no_saf_ansps > 2)}
#| echo: false
mycharts[[3]]
```
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != "SES RP3") & (params$no_saf_ansps > 3)}
#| echo: false
mycharts[[4]]
```
:::::: 
:::::
`r if (params$country == "SES RP3" | params$no_saf_ansps != 4) "::::"`


`r if (params$country != "SES RP3") ":::: {.content-hidden}"`
```{r chart_level2_saf_eosm_ses_allstates, eval= params$country == "SES RP3"}
#| file: R/chart_level2_saf_eosm_ses_allstates.R
#| out.width: "100%"
```

::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r chart_level2_saf_eosm_count_ses, eval= params$country == "SES RP3"}
#| file: R/chart_level2_saf_eosm_count_ses.R
#| out.width: "100%"
```
:::::: 

:::::: {.chart-container}  
```{r chart_level2_saf_maturity_count_ses, eval= params$country == "SES RP3"}
#| file: R/chart_level2_saf_maturity_count_ses.R
#| out.width: "100%"
```
:::::: 
:::::

`r if (params$country != "SES RP3") "::::"`


`r if (params$country == "SES RP3") ":::: {.content-hidden}"`
:::: {.callout-note collapse=true}

#### Focus on EoSM

`r saf_text`

::::
`r if (params$country == "SES RP3") "::::"`


`r if (params$country == "MUAC") ":::: {.content-hidden}"`

## Rate of runway incursions (RIs) (PI#1)

:::: {layout="[ 45, 55 ]"}
::::: {.chart-container}  
```{r chart_saf_ri, eval= params$country != "MUAC"}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_level2_saf_ri_year_report, eval= (params$country != "MUAC"), options = (safindicator=c("ri"))}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```
:::::
::::

`r if (params$country != "SES RP3") ":::: {.content-hidden}"`
```{r chart_level2_saf_ri_per_state_ses, eval= (params$country == "SES RP3")}
#| file: R/chart_level2_saf_ri_per_state_ses.R
#| out.width: "100%"
```

```{r table_level2_saf_ri_apt_ses, eval= (params$country == "SES RP3")}
#| file: R/table_level2_saf_ri_apt_ses.R
#| out.width: "100%"
```
`r if (params$country != "SES RP3") "::::"`


:::: {layout="[ 20, 60, 20 ]"}
::::: {#emptydiv}  
:::::

::::: {.chart-container}  
```{r table_level2_saf_ri_apt, eval= (params$country != "MUAC") & (params$country != "SES RP3")}
#| file: R/table_level2_saf_ri_apt.R
#| out.width: "100%"
```
:::::

::::: {#emptydiv}  
:::::
::::

`r if (params$country == "MUAC") "::::"`

## Rate of separation minima infringements (SMIs) (PI#2)

:::: {layout="[ 45, 55 ]"}
::::: {.chart-container}  
```{r chart_saf_smi}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi"))}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```
:::::
::::

```{r table_level2_saf_smi_ansp}
#| file: R/table_level2_saf_smi_ansp.R
#| out.width: "100%"
```


`r if (params$country == "SES RP3") ":::: {.content-hidden}"`

## Quality of occurences reporting 

placeholder for text

## Use of automated safety data recording system (ASDRS) (PI#3)

:::: {layout="[ 25, 50, 25 ]"}
::::: {#emptydiv}  
:::::

::::: {.chart-container}  
```{r table_level2_saf_autotools, eval= (params$country != "SES RP3")}
#| file: R/table_level2_saf_autotools.R
#| out.width: "100%"
```
:::::

::::: {#emptydiv}  
:::::
::::

`r if (params$country == "SES RP3") "::::"`

:::





