[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
First normal year after COVID19, when traffic reached 2019 level.<br/>Capacity target achieved.

### Monitoring process for capacity performance
No specific monitoring in place, no delays caused by Ljubljana ACC.

### Capacity Planning
Planned capacity in line with NM requirements.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
Low amount of additional traffic due to lack of capacity in neighbouring (east side) ACCs.

### Summary of capacity performance
The Ljubljana FIR experienced an increase in traffic from 279k flights in 2021, to 453k flights, with practically zero ATFM delays. Traffic levels were almost nack to the 460k flights observed in 2019.