[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
The value for en route ATFM delay per flight presented here is subsequent to the NM post operations delay attribution process.
:::
::::


### NSA's assessment of capacity performance
Despite ongoing effects of the COVID-19 pandemic, traffic started to return with particularly and unexpectedly high figures during the summer period. Staff availability was still impaired by various waves of the pandemic, yet the provision of ANS was not severely impacted. <br/><br/>Capacity targets were met despite the return of traffic, shifted traffic flows due to the Russian war of agression against Ukraine and ongoing COVID effects on staff availability.

### Monitoring process for capacity performance
Apart from permanent ATFCM processes in place, monitoring traffic during the strategic, pretactical, and tactical phase as well as post OPS analyses are regularly executed.  Furthermore, a daily, weekly, monthly, yearly monitoring of capacity and delay is executed.

### Capacity Planning
Based on NM TFC predictions (STATFOR, NOP), capacity is planned and managed in terms of sector opening hours based inter alia on human resources and traffic distribution.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
Not applicable.

### Summary of capacity performance
Austria experienced an increase in traffic from 739k flights in 2021 to 1267k flights in 2022; however, traffic levels were still below the 1,365k flights in 2019. <br/><br/>In 2022, Austro Control had 78k minutes of en-route AFTM delay, up from <1k minutes of delay in 2021. However, in 2019 when Austria had 1365k flights, Austro Control had more than 1530k minutes of delay.<br/><br/>There were an additional 27k minutes of en route ATFM delay originating in the Vienna ACC that were re-attributed to DFS (>17k) and DSNA (>9k) via the NM post operations delay attribution process, according to the NMB agreement for eNM/S22 measures, to ameliorate capacity shortfalls in both Karlsruhe UAC and Reims ACC.