[3 Capacity]{class="fakeh1"}

## 3.1 En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
The value for en route ATFM delay per flight presented here is subsequent to the NM post operations delay attribution process.
:::
::::


### NSA's assessment of capacity performance
2022 en route capacity target set in the Swiss National performance plan was just not met for 2022 (total ATFM-Delay per flight : 0.21 min/fl., 0.02 min. above the target).  The delay in 2022 was mainly caused by severe adverse weather conditions above the Alps, limited ATC capacity and to a lesser extent, staffing. 
High uncertainty on traffic recovery over medium term horizon (2-3 months), new traffic patterns and increased volatility had also an aggravating impact during the Summer period.  
In 2022, Skyguide just missed its total en-route ATFM delay per flight. The main cause of delays were Weather (45%), ATC-Capacity (32%), Staffing (8%), Equipment (ATC) (7%), Other (6%) and Special Event (1%).
Before applying the post-ops adjustment process, the total en-route ATFM delay per flight reached 0.34 min / flight whereas the CRSTMP En-route ATFM delay per flight reached 0.15 min / flight as shown in the Capacity Report of the FABEC. After applying the post-ops adjustment process and re-attributing respectively 61 357 min to DSNA and 49 178 min to DFS according to the NM data, skyguide reached 0.21 for the total en-route ATFM delay per flight and 0.11 for the CRSTMP part. 
The main cause of delay was weather. As Skyguide is in charge of air traffic control in the centre of the Alps, it is a lot more subject to strong adverse weather conditions than the major part of all the other ANSPs. 
As a basis for comparison,  the NM includes approximately 15% of delay due to Weather in its delay forecast. The fact that heavy CB situation begins to occur in May until September is obviously an aggravating factor as it happens exactly at the same time as the yearly peak of traffic demand, which has a tremendous impact on delays.

### Monitoring process for capacity performance
The monitoring for en-route capacity performance is carried out under the auspices of the FABEC Financial and Performance Committee (FPC), counterpart of the European Commission at the States side, consulting and reporting to FABEC Council as appropriate.
On a monthly basis and through the AFG/PMG (ANSP FABEC Group / Performance Management Group) the ANSPs  collectively submit a report to the FPC, based on PRU available data, consolidated and analysed, on their joint progress in achieving the national target set and reference or indicative values and on the results and analysis of the en- route capacity achievement.
In case the national target set and/or the annual/reference values are threatened not to be met, AFG/PMG is asked to propose to FPC possible corrective measures which the ANSPs determine fit to react to the weaker performance at  national and/or ACC level, in order to remedy the situation. 
The FPC analyses the reports, assesses the actions considered by the ANSPs together with the necessity of appropriate measures to be taken by the States or the NSAs and makes an advice to the proposals, made by the AFG/PMG, to the FABEC Council for such appropriate measures, after consultation with the AFG/PMG. The potential corrective measures take  into account the seriousness of the risk of not meeting the targets set and/or the annual/reference values.
The FPC is also responsible for the management of the Capacity KPA financial incentive schemes. This monitoring process is described in the FABEC FPC States Performance Process description, regularly updated.
The Swiss NSA has periodical meetings with its ANSPs. -  The Swiss NSA is regularly provided with various reports, analysis and data such as FABEC monthly capacity reports (including Skyguide data), Skyguide reports, PRU dashboards which enable to closely monitor the performance evolution.

### Capacity Planning
A NOP Recovery Plan process was initiated and launched by the Network Manager and its first edition was published on 30 April 2020, as European traffic began a slow recovery from its lowest point of just 2,099 flights across the network on 12 April 2020. 
Since then a weekly Rolling NOP, published every Friday has been introduced through which NM coordinates with all partners to ensure capacity is available at ACCs and in the airspace they manage, and on the ground at airports, to meet the expected traffic demand from the airlines on each day of the next six weeks enabling to coordinate all operational stakeholders throughout the pandemic to ensure that network actors can plan their recovery effectively based on predicted traffic levels.
On 6th May 2022, a first version of the new 2022-2026 NOP has been released (still based on the STATFOR forecast published in October 2021 as STATFOR has postponed the publication of its new forecast to October 2022). It  included the capacity planning for skyguide with the latest available capacity information and remedial measures for all ACCs  concerned by capacity issues.
 
Skyguide is of course part of this process and contributes to the provision for a consolidated European network view of the evolution of the air traffic, enabling the planning of the service delivered in the recovery phase to match the expected air traffic demand in a safe, efficient and coordinated manner. However, the 10% capacity buffer requested by the NM, the recommendation for zero delay and the continuous optimistic traffic forecast selected have naturally an adverse impact on ANSPs finance.
Skyguide implemented the cross-border airspace restructuring with Reims ACC and Basel APP, improved ATFCM procedures and STAM as well as the CDM procedures for Airspace requests level 2 and 3 (ASM - ATFCM), its optimized sector opening scheme to match the traffic demand, network weather mitigation measures, the FABEC airspace structure and implemented the FRA CH.
 
In parallel, Skyguide continued to develop its top priority programme: the Virtual Centre; in addition, Crystal, the traffic and complexity prediction tool is continuously improved.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
A CAPAN (Capacity analysis) study has been planned in both ACCs, starting at the end of 2022, results will be available at the end of Summer 2023, and capacity should be increased before Summer 2024​.
Short-term ATFCM measures and what-if scenarios: in 2023, Skyguide implemented fully coordinated flow based measures between both centres Geneva and Zurich. It allows to diminish delay avoiding regulations when we observe excess of demand over short-period of time and allows to increase flight efficiency when we have a capacity surplus and we can relieve RAD constraints (offering greener trajectories)​.
Increase usage of CPDLC: the use of CPDLC is particularly scrutinized, simulations have been led to quantify the possible benefits. Within the course of 2023, analyses will be led to determine to which extent some of the CPDLC performance enhancement impacts could be harvested through an increase of sector capacity.
Finally, Skyguide will launch a trial in Summer 2023 with a new tool to detect more precisely the impact of adverse weather conditions on the required temporary decrease of sector capacity.

### Summary of capacity performance
Switzerland did not achieve the required en route capacity performance in 2022. There were 1 042k  flights in the airspace of Switzerland, with 242k minutes of ATFM en route delay attributed to Skyguide after the NM post operations delay attribution process.
There were an additional 111k minutes of en route ATFM delay originating from Skyguide that were re-attributed to DFS (>49k) and DSNA (>61k) via the NM post operations delay attribution process, according to the NMB agreement for eNM/S22 measures, to ameliorate capacity shortfalls in both Karlsruhe UAC and Reims ACC.