[3 Capacity]{class="fakeh1"}

## 3.1 En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
In the beginning of 2022 traffic was just recovering from Covid-19 until the end of February when the traffic almost ceased in Finland. The war in Ukraine; the closure of Russian airspace; and banning Russian airlines from flying in Finnish airspace, had a huge impact in traffic. 
As a result of the sanctions, all European airlines stopped flying to Asia completely over Finland. In general, overflying traffic was around 60 % of the level of 2019. Finnair, the biggest customer to Fintraffic ANS, was forced to change its strategy after the end of Russian overflights to Asia. Traffic to Kaliningrad increased over the international waters between Estonia and Finland. This traffic increase can be noticed in the number of operations but its impact in terms of service units is less. 
Finland reached the capacity targets in both KPIs, en-route and terminal. En-route delays have been zero in many years, and the capacity provided for this is due to user demand for as few delays as possible.
The en-route overflying traffic between Europe and Asia has dropped dramatically due to the war and the related airspace closure, and has resulted to continuation of some of the temporary staff lay-offs.

### Monitoring process for capacity performance
Review of the actual values from the NM dashboard.

### Capacity Planning
En-route ATFM delay will remain low as the capacity is delivered due to user demand.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
There are changes in traffic flows/patterns: airspace closures have shifted the traffic flows from Russia to Kaliningrad, and these flights have to use the narrow international airspace corridor between Finland and Estonia, and can not use the direct routing that has been used before the war. There is an average of 350 flights per week.
Also the flights from Europe to Asia are not overflying Finnish airspace anymore because of the airspace closure.
Another change is in the flights between Finland (Helsinki) and Japan, where our main operator Finnair flies daily. These flights can't fly the most direct route anymore because of the airspace closure, and have to fly via northern route above the North Pole. 
These changes do not affect the en route capacity performance, but still need to be taken into account when assessing the overall performance of the ANSP.

### Summary of capacity performance
Finland experienced an increase in traffic from 123k flights in 2021, to 205k flights in 2022; again, with zero ATFM delay. However, traffic levels were still substantially below the 285k flights in 2019.