[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
After two years of COVID-19 pandemic, along with the other Baltic states, Latvia was hot by the aftermath of Russian invasion in Ukraine. Sanctions imposed by EU, along with the sanctions imposed by Russia against EU, changed the traffic flows dramatically.<br/><br/>Traffic flow between Russia to Europe stopped, while the Europe ↔ China and Europe ↔ SE Asia segments dramatically dropped. Due to restrictions on overflying EU airspace, Russian aircraft operators started to fly over  high seas in the Baltic sea in order to connect Kaliningrad to mainland Russia. This increased the traffic in Latvian delegated airspace, but has a negative impact on the receivables of the ANSP.<br/><br/>Due to Russian invasion in Ukraine and the EU sanctions against the Russia and Belorussia, air traffic flows have remained at approximately 60% of 2019 air traffic level. <br/><br/>No capacity issues have been identified.

### Monitoring process for capacity performance
Capacity monitoring takes place during annual inspections, in addition to regular monthly statistical data sent by the LGS to the LV CAA.

### Capacity Planning
Capacity planning measures by LGS are checked during annual inspections.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
Not applicable

### Summary of capacity performance
Latvia experienced an increase in traffic from 163k flights in 2021, with zero ATFM delay, to 190k flights in 2022, also with zero en route ATFM delay. <br/><br/>Traffic levels were still substantially below the 295k flights in 2019.