[3 Capacity]{class="fakeh1"}

## En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
The COVID-19 pandemic has had significant impact on the aviation industry in 2020/2021 while bounce back of the traffic in FIR Zagreb was among highest in the Europe resulting in the actual traffic being at the 2019 level, whilst traffic during 2022 summer season (May – September) was 4% higher than in the same period of the 2019. <br/><br/><br/>The ANSP did not meet the set CAP target due to the significant increase of traffic in LDZO ACC where actual traffic was 42% higher than planned in the RP3 Performance plan. As a consequence, limitations occurred during summer season due to unplanned high increase of traffic demand in peak hours.<br/><br/>Croatian Civil Aviation Agency has established an agreement with CroControl ltd. to convene bianually as part of the performance monitoring process. If the need is determined, a meeting can be organized to discuss the identified issues and/or discrepancies. Croatian Civil Aviation Agency identifyed the factors that directly affected the increase in minutes of delay compared to what was planned in the performance plan. Recognized factors are:<br/><br/>1. Traffic Levels – The target delay values were determined based on STATFOR's traffic forecast from May 2021, specifically the Base scenario. According to that specific forecast, Croatia was expected to have 501,000 flights in 2022. However, EUROCONTROL's NOP document (2022-2026) considered the STATFOR forecast from October 2021, which indicated that it was realistic to anticipate traffic levels higher than the High scenario of traffic demand. In other words, Croatia was projected to have approximately 700,000 flights. By the end of 2022, CroControl Ltd. recorded over 700,000 flights, which represents a 40% increase in traffic compared to the forecasted levels at the time when the performance plan targets were established.<br/><br/>Furthermore, the South-East Axis stands out as a transportation corridor that experienced the swiftest and most significant recovery of traffic at the European level following the COVID restrictions. This can be exemplified by comparing traffic levels in 2019 with those in 2022. According to data from the Aviation Intelligence Portal, Croatia had only 1,000 fewer flights in 2022 compared to 2019.<br/><br/>2. Number of Available ATCOs – In August 2022, there was an unexpected departure of controllers due to eight resignations classified as extraordinary. Additionally, one individual requested to cease working in operations for personal reasons. <br/><br/>3. Priority of Training for new ATCOs – CroControl Ltd. places high priority on the training of controllers. Consequently, during the summer season, eight ATCO instructors were assigned to provide simulator training to new controllers as part of the ATCO TO program.

### Monitoring process for capacity performance
Monitoring of all available KPI's and PI's is done through the Single European Sky Data Portal which is considered as the main source of information.<br/><br/>In the year 2022 there were significant challenges for LDZO ACC capacity KPI as the actual traffic was 42% higher than planned in the RP3 Performance plan while summer season traffic was 4% above historical highest year (2019). As a consequence, limitations occurred during summer season due to unplanned high increase of traffic demand in peak hours.

### Capacity Planning
Capacity planning is done in line with NM’s initiative for development of a rolling NOP document in which short-term capacity and demand on the Network level is described. The expected traffic outlook is given for eight weeks ahead and revised weekly, while capacity is adapted to traffic demand and reported to NM which assesses the efficiency for planned period. In the planning process on local level, several departments are involved in strategic and tactical development of the plan.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
The shortage of air traffic controllers is a recognized problem that is being continuously addressed. Sector capacities and available staff have been communicated with the Network Manager, and on a daily basis, additional management of available capacities is carried out to optimize the utilization of resources to the fullest extent possible.<br/><br/>CroControl ltd. has re-evaluated its sector capacities in late 2022 in order to optimize available resources. The new sector capacity values have been in effect since March 6, 2023.<br/><br/>Furthermore, CroControl ltd. continuously improves its ATS system, staff training, and sharing of best practices which has resulted in significantly more efficient utilization of existing capacities. This is evidenced by comparing traffic and delays in June and July 2022 to the same period in 2019. <br/><br/>In late 2022, a refreshment course for FMP personnel was conducted, and in 2023, CroControl ltd., in collaboration with EUROCONTROL, has agreed to share best practices in preparation for the summer period.

### Summary of capacity performance
Croatia experienced an increase in traffic from 461k flights in 2021 to 713k flights in 2021, compared to 714k flights in 2019. <br/><br/>Actions taken and results of improved capacity performance are visible in the handling of traffic during June 2022. In June 2022 Croatia had 24k minutes of ATFM delay while handling more than 80k flights.<br/>For comparison in June 2019 approximately 79k flights resulted in around 97k minutes of delay.