[3 Capacity]{class="fakeh1"}

## 3.1 En route
### Minutes of ATFM en-route delay

:::: {.columns}
  
::: {.column width="55%"}

```{r}
#| file: R/table_cap_er_1.R
#| out.width: "100%"
```
:::

::: {.column width="1%"}
:::

::: {.column width="44%"}

**Observations**
NA
:::
::::


### NSA's assessment of capacity performance
Cyprus is in a turbulent region of the world, where geopolitical changes are frequent and, often, dramatic. For this reason, air traffic volatility is very high and traffic demand estimates (hence, ATM performance) can vary as a result of external factors.  These factors are beyond the control of the ANSP and the State in general.
Furthermore, geopolitical changes can significantly alter the air traffic flows, creating new hotspots and signigificant capacity constraints. As an example, the Russia - Ukraine conflict has removed a significant traffic flow (and associated revenue) to and from Cyprus. As another example, the categorisation, by EASA, of the Syrian airspace as "conflict zone" has eliminated traffic flows in the north-eastern part of Nicosia FIR. These flows were diverted to the south, saturating the west and south sectors of Nicosia ACC.
Capacity performance improved significantly in 2022. However, air traffic demand in 2022 was still lower than the 2019 levels. In this respect, the 2022 results cannot be considered as an accurate indication of future trends.

### Monitoring process for capacity performance
The NSA has in place the "NSA procedure for the monitoring of ANS Performance". According to this procedure, the NSA monitors at quarterly intervals the average minutes of enroute ATFM (Air Traffic Flow Management) delay per flight. Based on this, the NSA analyzes the trends and takes the necessary measures, if needed.

### Capacity Planning
Capacity planning is done with the Network Manager and is consistent with the required performance.
The transfer to the new ACC, which is delayed and planned in late 2023 to mid 2024, is expected to be the source of air traffic delays, which however will be of temporary nature.  As the transfer will be done during a low traffic period the effect on the European Network is not expected to be significant. Efforts will be made so that any operation related to the transfer i.e. shadowing operations will be kept to the absolute minimum level so not to absorb HR from the actual ops at the new ACC.

### ATCO in OPS (FTE)

```{r}
#| file: R/table_cap_er_2.R
```
```{r}
htmltools::tagList(t)
```



### Application of Corrective Measures for Capacity (if applicable)
Nil

### Summary of capacity performance
Cyprus experienced an increase in traffic from 252k flights in 2021, to 344k flights in 2022, with practically zero ATFM delay. However, traffic levels were still substantially below the 411k flights in 2019.