##  Military dimension
### Update on Military dimension of the plan

Military dimension has little to no impact on the environmental KPA, due to a highly efficient and flexible use of airspace with close military coordination.<br/><br/>Practically no impact of MIL dimension on the capacity KPA.<br/>The planning of airspace use at pre-tactical level is done via the civil/military joint unit Airspace Management Cell<br/>(AMC). Day-to-day co-ordination of Operational Air Traffic (OAT) and General Air Traffic (GAT) is handled at the tactical level between civil ATS Units and representatives of the Military Control Centre (MCC).<br/>FUA Level 3 is fully applied.

### Military - related measures implemented or planned to improve capacity

n/a

### PI#6 Effective use of reserved or segregated airspace - national level

```{r,  options=(range = "B15:N17")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r,  options=(range = "B20:N29")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

Preparations for LARA implementation are set, which is planned for operational use by end 2023.

### PI#7 Rate of planning via available airspace structures - national level

```{r,  options=(range = "B37:N39")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r,  options=(range = "B42:N51")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

nothing reported

### PI#8 Rate of using available airspace structures - national level

```{r,  options=(range = "B59:N61")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r,  options=(range = "B64:N73")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

Not yet measured, as CDRs are not in place, and due to extremely flexible usage of airspace, nearly all aircraft planning through reserved area are able to do so.<br/>Only a few aircraft might be subject to minor reroutings (horizontal / vertical).