## 2.3 Military dimension
### Update on Military dimension of the plan

NA

### Military - related measures implemented or planned to improve capacity

NA

### PI#6 Effective use of reserved or segregated airspace - national level

```{r}
#| file: R/table_env_mil_1.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r}
#| file: R/table_env_mil_2.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

LARA/PRISMIL implemented, automated reporting, that differs from manual calculation that was used earlier in 2020, 2021 and RP2.
The figures for 2020 and 2021 should be as follows: 
2020 number of hours allocated & notified: 38340; used: 34296 (ratio 89,45%)
2021 number of hours allocated & notified: 37346; used: 33978 (ratio 90,98%)

### PI#7 Rate of planning via available airspace structures - national level

```{r}
#| file: R/table_env_mil_3.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_4.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

LARA/PRISMIL implemented, automated reporting, that differs from manual calculation that was used earlier in 2020, 2021 and RP2.
Figures for 2020 and 2021 should be as follows:
2020 number of aircraft filing via reserved or segregated airspace and CDRs: 1676883; could have planned: 1779163 (ratio 94,25%)
2021 number of aircraft filing via reserved or segregated airspace and CDRs: 1908679; could have planned: 1982855 (ratio 96,26%)

### PI#8 Rate of using available airspace structures - national level

```{r}
#| file: R/table_env_mil_5.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_6.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

LARA/PRISMIL implemented, automated reporting, that differs from manual calculation that was used earlier in 2020, 2021 and RP2.
Figures for 2020 and 2021 should be as follows:
2020 number of aircraft flying via reserved or segregated airspace and CDRs: 1512596; could have planned: 1779163 (ratio 85,02%)
2021 number of aircraft flying via reserved or segregated airspace and CDRs: 1721982; could have planned: 1982855 (ratio 86,84%)