##  Military dimension
### Update on Military dimension of the plan

The analysis can not be provided due to reason that all required data for ENV PI #6, PI #7 and PI #8 are not yet available on the NM/PRU dashboards nor delivered by NM upon request. <br/><br/>During the preparation of the EUROCONTROL CAPAN study in 2022, it was recognized that military traffic has no significant impact on the sector capacities of the LDZO ACC.

### Military - related measures implemented or planned to improve capacity

FUA restrictions and CDRs have been implemented which are managed by AMC on ASM Level 2 and notified to NM but were sparsely used or required due to significant decrease of military activities and air traffic affected by COVID-19 crisis.<br/><br/>No remedial measures identified.

### PI#6 Effective use of reserved or segregated airspace - national level

```{r}
#| file: R/table_env_mil_1.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r}
#| file: R/table_env_mil_2.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

The Network Manager shall provide on a monthly basis the data required for the monitoring of this indicator for monitoring referred to Regulation (EU) 2019/317 point 6 of Annex VI.<br/><br/>The data regarding ratio of using available airspace structures has been received from NM upon request but the data regarding number of aircraft flying via reserved or segregated airspace and CDRs and number of aircraft that could have planned through those airspace structures have not been delivered by NM upon request nor such data are available on the NM/PRU dashboards.

### PI#7 Rate of planning via available airspace structures - national level

```{r}
#| file: R/table_env_mil_3.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_4.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

The Network Manager shall provide on a monthly basis the data required for the monitoring of this indicator for monitoring referred to Regulation (EU) 2019/317 point 6 of Annex VI.<br/><br/>The data regarding ratio of using available airspace structures has been received from NM upon request but the data regarding number of aircraft flying via reserved or segregated airspace and CDRs and number of aircraft that could have planned through those airspace structures have not been delivered by NM upon request nor such data are available on the NM/PRU dashboards.

### PI#8 Rate of using available airspace structures - national level

```{r}
#| file: R/table_env_mil_5.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_6.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

The Network Manager shall provide on a monthly basis the data required for the monitoring of this indicator for monitoring referred to Regulation (EU) 2019/317 point 6 of Annex VI.<br/><br/>The data regarding ratio of using available airspace structures has been received from NM upon request but the data regarding number of aircraft flying via reserved or segregated airspace and CDRs and number of aircraft that could have planned through those airspace structures have not been delivered by NM upon request nor such data are available on the NM/PRU dashboards.