##  Military dimension
### Update on Military dimension of the plan

No impact of military on capacity has been identified. Current decrease in air traffic due to sanctions on Russia and Belorussia and flexible arrangements between the LGS and the National Armed Forces allow for environmentally friendly flight trajectories and it reduces the impact to capacity. <br/><br/>**Additional information related to Russia's war of aggression against Ukraine**<br/>In general, military training activities have increased over the past years. At the same time, civmil airspace design and airspace use flexibility provisions between the NAF and LGS ensure that there's no impact on scheduled air traffic.<br/>New large military FUA areas over Eastern part of the Riga FIR, next to Russian Federation and Belorussia, have been established.

### Military - related measures implemented or planned to improve capacity

Each new long term or short term area for military purposes undergoes airspace design analysis with respect to impact on major air traffic flows as to not to disrupt them or to change their vertical dimensions dynamically, if necessary.<br/><br/>Close cooperation between Latvian ANSP and the Latvian military.

### PI#6 Effective use of reserved or segregated airspace - national level

```{r,  options=(range = "B15:N17")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r,  options=(range = "B20:N29")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

Existing  LGS and NAF airspace booking and airspace use procedures are continuously being updated.  This data includes all FUA areas, including those being active for 24/7 for longer periods of time, but not on continuous basis. Due to involvement of military units from different countries, individual airspace planning and airspace use capabilities are not the same each year and do not ensure the same consistent performance in airspace use, even if planned through the Latvian NAF.  <br/>The results of the assessment are also shared with the Military Aviation Administration for further review.

### PI#7 Rate of planning via available airspace structures - national level

```{r,  options=(range = "B37:N39")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r,  options=(range = "B42:N51")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

FRA has been implemented in 2015.

### PI#8 Rate of using available airspace structures - national level

```{r,  options=(range = "B59:N61")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r,  options=(range = "B64:N73")}
#| file: R/table_env_mil.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

FRA in Riga FIR was implemented in 2015.