## 2.3 Military dimension
### Update on Military dimension of the plan

The air navigation services in Nicosia FIR are provided with reference to the arrangements which have been established through the implementation of regulation (EC) 2150/2005 “laying down common rules for the flexible use of airspace”. (see section 5, Application of FUA)

The implementation of the said Regulation has been achieved through the adoption of the “National Plan for the Implementation of FUA”, signed on the 2nd of July 2009. The implementation of the National FUA plan ensures to the maximum possible extent, the most efficient use of airspace, both by civil and military users. 

The activities of the National Military Authorities are predominately executed over the National airspace. The cooperation between the national Civil and Military Authorities is excellent and the effect on civil aviation is minimal. 

Over the high seas however, which constitute the majority of the Nicosia FIR, a number of foreign Military authorities, most commonly the Russian Navy, USA Navy, French Navy, Israeli Air Force, British Air Force and  Turkish military forces,  regularly performed operational flights and exercises throughout 2022.  Additionally, air carrier operations in Nicosia FIR combined with the different military authorities made it necessary to implement and upgrade the coordination among the willing authorities.

The activities of the British and Israeli forces were coordinated fairly well with the national authorities (AMC) keeping the adverse effect on ATS to minimal effect. 

The most significant impact on ATS is caused by the refusal of the Turkish authorities to coordinate or cooperate with Cyprus on the conduct of any military activities in Nicosia FIR. Turkish activity NOTAMS are issued by non-authorised entities relevant to these activities thus imposing a significant level of uncertainty on ATM management in Nicosia FIR adversely affecting capacity. A regular phenomenon is the penetration  of Nicosia FIR or  Cyprus National airspace in violation to  ICAO procedures thus increasing the workload on ATC staff and hence having a detrimental effect on airspace capacity.

The political unrest in the South East Mediterranean region gave rise to the number of USA and Russian operational flights (OAT). These flights were rarely coordinated with the ATS authorities thus causing additional workload to ACC staff. Nevertheless, the situation in 2022 was better than previous years, as a consequence of the COVID-19 pandemic, better coordination with British and Israeli military authorities, enhanced cooperation among AMC/ATC units and aircraft carriers operating in the area and fewer operations of aircraft carriers south of Cyprus.

The designation, by EASA, of the Syrian airspace as "conflict zone" has significantly affected the traffic flows in the north east part of Nicosia FIR.

### Military - related measures implemented or planned to improve capacity

There will be continuous efforts to improve further the coordination with third country military authorities using the Nicosia FIR.

### PI#6 Effective use of reserved or segregated airspace - national level

```{r}
#| file: R/table_env_mil_1.R
#| out.width: "100%"
```



### PI#6 Effective use of reserved or segregated airspace (per ACC)

```{r}
#| file: R/table_env_mil_2.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#6

The NSA verifies through audits and inspections that the entity responsible for the tactical management of the airspace (AMC), monitors the planned Vs the actual times of airspace reservations so as to promote the most effective use of reserved or segregated airspace. In the context of its oversight inspections it has raised findings in order to drive positive change and to optimise the application of FUA and, as a result, improvements have been noted. For example, real time activation / de-activation of reserved areas is now implemented through the establishment of real time communications between the ATC Units and Military authorities.

### PI#7 Rate of planning via available airspace structures - national level

```{r}
#| file: R/table_env_mil_3.R
#| out.width: "100%"
```



### PI#7 Rate of planning via available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_4.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#7

PRISMIL CURA has been implemented by Cyprus AMC in early 2023. All the data provided are according to the data available on PRISMIL.

### PI#8 Rate of using available airspace structures - national level

```{r}
#| file: R/table_env_mil_5.R
#| out.width: "100%"
```



### PI#8 Rate of using available airspace structures (per ACC)

```{r}
#| file: R/table_env_mil_6.R
#| out.width: "100%"
```


### Initiatives implemented or planned to improve PI#8

PRISMIL CURA has been implemented by Cyprus AMC in early 2023. All the data provided are according to the data available on PRISMIL.