```{r context-data, eval=TRUE}
cztype = "enroute"
cz = c("1", "enroute")

data_muac  <-  read_xlsx(
  paste0(data_folder, "CEFF dataset master.xlsx"),
  sheet = "Enroute_T1",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() |> 
  filter(grepl("MUAC", entity_code), status == "A", year == year_report) |> 
  mutate(
    entity_code = str_replace_all(entity_code, "_EB", ""),
    entity_code = str_replace_all(entity_code, "_EL", "")
    ) |> 
  group_by(year, entity_code) |> 
  summarise(x5_3_cost_nc2017 = sum(x5_3_cost_nc2017, na.rm = TRUE)) |> 
  ungroup()

total_muac_costs <- sum(data_muac$x5_3_cost_nc2017, na.rm = TRUE)

share_EBEL <- paste0(round(pull(select(filter(data_muac, entity_code == "EBEL_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")
share_ED <- paste0(round(pull(select(filter(data_muac, entity_code == "ED_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")
share_EH <- paste0(round(pull(select(filter(data_muac, entity_code == "EH_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")

```


<!-- ## Safety -->

```{r chart_eosm, include=FALSE, options = (doclevel=c("level1"))}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```

<!-- ## Capacity -->

```{r chart_cap_er, include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

<!-- ## Cost-efficiency -->

```{r chart_cef, include=FALSE}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```

<!-- Level2 -->
<!-- ## Safety L2-->
<!-- ### Rate of separation minima infringements (SMIs) (PI#2) -->

```{r chart_saf_smi, include=FALSE}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```

```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

```{r table_level2_saf_smi_ansp_pdf1}
mytable <-"table_level2_saf_smi_ansp_pdf1"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

```{r table_level2_saf_smi_ansp_pdf2}
mytable <-"table_level2_saf_smi_ansp_pdf2"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- ### Use of automated safety data recording system (ASDRS) (PI#3) -->

```{r table_level2_saf_autotools}
mytable <-"table_level2_saf_autotools"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```


<!-- ## Capacity L2-->
<!-- ### En route performance -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- #### Other indicators -->
```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_atco_acc, include=FALSE}
#| file: R/chart_level2_cap_atco_acc.R
#| out.width: "100%"
```

<!-- ## Cost-efficiency -->

```{r chart_cef_cost_muac, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```

```{r table_cef_cost_muac, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cost"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- END OF CHARTS AND TABLES -->


```{=tex}
\setlength{\fboxrule}{0pt} % Set the border width to 0pt (no border)
\setlength{\fboxsep}{0pt} % Remove padding
```

# OVERVIEW

## Contextual information

```{=latex}
\begin{figure}

\small

\begin{minipage}[t]{0.35\linewidth}

\textbf{Provision of ATC services in the upper}  \\
\textbf{airspace across four States}
\\
\\

\textbf{ACC}\hspace*{1cm} Maastricht UAC

\end{minipage}%
\begin{minipage}[t]{0.25\linewidth}

Belgium/Luxembourg  \\
Germany  \\
Netherlands

\end{minipage}%
\begin{minipage}[t]{0.40\linewidth}

\textbf{Allocation of actual en route costs} \\

\begin{minipage}[t]{0.70\linewidth}

• Belgium/Luxembourg  \\
• Germany  \\
• Netherlands

\end{minipage}%
\begin{minipage}[t]{0.30\linewidth}
```

`r share_EBEL`  
`r share_ED`  
`r share_EH`

```{=latex}
\end{minipage}%

\end{minipage}%

\end{figure}
```

## Safety

```{r concl-eosm}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
saf_text_conc <- break_l1_text(saf_conc1) 
saf_text1 <- saf_text_conc$text1
saf_text2 <- saf_text_conc$text2
```

`r paste0(layout_wrap_figure("chart_eosm", NULL, saf_text1, 15), saf_text2)`

## Capacity

```{r concl-cap}
cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
cap_er_text_conc <- break_l1_text(cap_er_conc1) 
cap_er_text1 <- cap_er_text_conc$text1
cap_er_text2 <- cap_er_text_conc$text2
```

`r paste0(layout_wrap_figure("chart_cap_er", NULL, cap_er_text1, 13), cap_er_text2)`


## Cost-efficiency

```{r concl-cef}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
cef_text <- break_l1_text(cef_conc1) 
cef_text1 <- cef_text$text1
cef_text2 <- cef_text$text2
```

`r paste0(layout_wrap_figure("chart_cef", NULL, cef_text1, 12), cef_text2)`

\needspace{3\baselineskip}

# SAFETY - `r toupper(params$country)`

## PRB monitoring

`r saf_conc1`

\needspace{2\baselineskip}

## Effectiveness of Safety Management (EoSM) (KPI#1)

```{r chart_saf_eosm, options = (doclevel=c("level2"))}
#| file: R/chart_level1_saf.R
#| out.width: "62%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

`\biggertext{Focus on EoSM}`{=latex}

`r latex_linebreaks(saf_eosm_text)`

\needspace{2\baselineskip}

## Safety occurrences

### Rate of separation minima infringements (SMIs) (PI#2)

`r layout_2fig("chart_saf_smi", "chart_level2_saf_smi_year_report")`

`r layout_summary_table(table_level2_saf_smi_ansp_pdf1, hspace = 0, left_margin = 0, width = 1)`

\vspace*{-0.5cm}

`r layout_summary_table(table_level2_saf_smi_ansp_pdf2, hspace = 0, left_margin = 0, width = 1)`

\needspace{3\baselineskip}


\biggertext{Focus on separation minima}

`r latex_linebreaks(saf_smi_text)`


\needspace{2\baselineskip}

### Quality of occurences reporting 

`r latex_linebreaks(saf_qr_text)`

\needspace{2\baselineskip}


# CAPACITY - `r toupper(params$country)`

## PRB monitoring

`r cap_er_conc1`

\needspace{3\baselineskip}

## En route performance

### En route ATFM delay (KPI#1)

`r layout_2fig("chart_cap_er_l2", "chart_cap_er_month")`

\needspace{3\baselineskip}

### Other indicators

`r layout_2fig("chart_cap_atco", "chart_cap_atco_acc")`

```{r chart_cap_sector_opening}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

# COST-EFFIENCY - `r toupper(params$country)`

## PRB monitoring

`r cef_conc1`

\needspace{3\baselineskip}

## Total costs

`r layout_fig_table("chart_cef_cost_muac", table_level2_cef_cost, vspace = -3.8)`
