<!-- ## Safety (Network Manager - SES RP3 area) -->

```{r chart_eosm, include=FALSE}
#| file: R/chart_level1_saf_nm.R
#| out.width: "100%"
```

```{r chart_deliveries, include=FALSE}
#| file: R/chart_level1_saf_deliveries_nm.R
#| out.width: "100%"
```


<!-- ## Environment (Network Manager - SES RP3 area) -->

```{r chart_env_kea, options = (doclevel=c("level1")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```


<!-- ## Capacity (Network Manager - SES RP3 area) -->

```{r chart_cap_er, include=FALSE}
#| file: R/chart_level1_cap_er_nm.R
#| out.width: "100%"
```

```{r chart_cap_trm, include=FALSE}
#| file: R/chart_level1_cap_trm_nm.R
#| out.width: "100%"
```

```{r chart_cap_15m, include=FALSE}
#| file: R/chart_level1_cap_15m_nm.R
#| out.width: "100%"
```

<!-- ## Cost-efficiency (Network Manager - SES RP3 area) -->

```{r chart_cef, include=FALSE}
#| file: R/chart_level1_cef_nm.R
#| out.width: "100%"
```


<!-- END OF CHARTS AND TABLES -->

```{=tex}
\setlength{\fboxrule}{0pt} % Set the border width to 0pt (no border)
\setlength{\fboxsep}{0pt} % Remove padding
```

# OVERVIEW

*`r pp_version`*

## Safety (Network Manager - SES RP3 area)

```{r concl-eosm}
saf_conc1 <- get_prb_conclusions("NM findings.xlsx", "NM_findings_EoSM", "NM_findings_EoSM")
```

`r layout_wrap_figure("chart_eosm", NULL, saf_conc1, 12)`


```{r concl-deliveries}
saf_conc2 <- get_prb_conclusions("NM findings.xlsx", "NM_findings_over", "NM_findings_over")
```

`r layout_wrap_figure("chart_deliveries", NULL, saf_conc2, 12)`


## Environment (Network Manager - SES RP3 area)

```{r concl-env}
env_conc1 <- get_prb_conclusions("NM findings.xlsx", "NM_findings_KEP", "NM_findings_KEP")
```

`r layout_wrap_figure("chart_env_kea", NULL, env_conc1, 12)`


## Capacity (Network Manager - SES RP3 area)

```{r concl-cap}
cap_er_conc1 <- get_prb_conclusions("NM findings.xlsx", "NM_findings_CAP", "NM_findings_CAP")
```

`r layout_wrap_figure("chart_cap_er", "chart_cap_trm", cap_er_conc1, 38, "chart_cap_15m")`


## Cost-efficiency (Network Manager - SES RP3 area)

```{r concl-cef}
cef_conc1 <- get_prb_conclusions("NM findings.xlsx", "NM_findings_CEFF", "NM_findings_CEFF")
```

`r layout_wrap_figure("chart_cef", NULL, cef_conc1, 12)`

