<!-- ### Traffic (SES RP3 area) L1 -->

```{r chart_level1_traffic_mvt, include=FALSE}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "100%"
```

```{r chart_level1_traffic_su, include=FALSE}
#| file: R/chart_level1_traffic_su.R
#| out.width: "100%"
```

<!-- ### Safety (SES RP3 area) L1 -->

```{r chart_level1_saf_ses, include=FALSE}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```

<!-- ### Environment (SES RP3 area) L1 -->

```{r chart_env_kea, options = (doclevel=c("level1")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```
<!-- ### Capacity (SES RP3 area) L1 -->

```{r chart_cap_er, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

<!-- ### Cost-efficiency (SES RP3 area) L1-->

```{r chart_level1_cef_er_ses, include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_trm_1, options = (cz=c("1", "terminal", "level1")), include=FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

<!-- Level2 text -->
```{r level_2_text}
source(here("R","get_level2_text.R"))
```

<!-- Level2 -->
<!-- ## Safety -->
<!-- ## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 -->
```{r chart_level2_saf_eosm_target_ses, include=FALSE}
#| file: R/chart_level2_saf_eosm_target_ses.R
#| out.width: "100%"
```


```{r chart_level2_saf_eosm_count_ses, include=FALSE}
#| file: R/chart_level2_saf_eosm_count_ses.R
#| out.width: "100%"
```

```{r chart_level2_saf_maturity_count_ses, include=FALSE}
#| file: R/chart_level2_saf_maturity_count_ses.R
#| out.width: "100%"
```

<!-- ### Occurrences - Rate of runway incursions (RIs) (PI#1)  -->

```{r chart_saf_ri, include=FALSE}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```

```{r chart_level2_saf_ri_year_report, options = (safindicator=c("ri")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ### Rate of separation minima infringements (SMIs) (PI#2) -->
```{r chart_saf_smi, include=FALSE}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```

```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ### En route performance -->
<!-- #### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2) -->

```{r chart_env_kea_l2, options = (doclevel=c("level2")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart_env_kea_month, include=FALSE}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```

```{r chart_env_kep_scr, include=FALSE}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart_env_kep_scr_month, include=FALSE}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```


<!-- ### En route performance -->
<!-- #### En route ATFM delay (KPI#1) -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
<!-- #### Other indicators -->

```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_sector_opening_ses, include=FALSE}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```

<!-- #### Arrival ATFM delay (KPI#2) -->
```{r chart_cap_trm_l2, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm_month, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route charging zone -->
```{r chart_cef_duc_er_ses, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_su, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```

```{r chart_cef_cost, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```

```{r table_cef_cost, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cost"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- AUCU -->
```{r chart_cef_aucu, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```

```{r table_cef_aucu, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_aucu"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

```{r chart_cef_cex, R.options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```

```{r table_cef_cex, R.options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cex"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- regulatory result -->
```{r chart_cef_reg_res, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu,  options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```


```{r saf_conc1}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
saf_text_conc <- break_l1_text(saf_conc1) 
saf_text1 <- saf_text_conc$text1
saf_text2 <- saf_text_conc$text2
```

# SAFETY - SES RP3

## PRB monitoring
```{r}
# saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024

`r layout_2fig("chart_level1_saf_ses", "chart_level2_saf_eosm_target_ses")`


```{r chart_level2_saf_eosm_ses_allstates}
#| file: R/chart_level2_saf_eosm_ses_allstates.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r layout_2fig("chart_level2_saf_eosm_count_ses", "chart_level2_saf_maturity_count_ses", width1 = 0.65, width2 = 0.30)`

\needspace{3\baselineskip}

\biggertext{Focus on EoSM}

`r latex_linebreaks(saf_eosm_text)`

\needspace{2\baselineskip}


## Rate of runway incursions (RIs) (PI#1)

`r layout_2fig("chart_saf_ri", "chart_level2_saf_ri_year_report")`

```{r chart_level2_saf_ri_per_state_ses}
#| file: R/chart_level2_saf_ri_per_state_ses.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r table_level2_saf_ri_apt_ses}
mytable <-"table_level2_saf_ri_apt_ses"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_level2_saf_ri_apt_ses, hspace = 0, left_margin = -1, width = 1.1)`

\needspace{3\baselineskip}


\biggertext{Focus on runway incursions}

`r saf_ri_text`

\needspace{2\baselineskip}


## Rate of separation minima infringements (SMIs) (PI#2)

`r layout_2fig("chart_saf_ri", "chart_level2_saf_smi_year_report")`

```{r chart_level2_saf_smi_per_state_ses}
#| file: R/chart_level2_saf_smi_per_state_ses.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```


```{r table_level2_saf_smi_ansp_pdf1}
mytable <-"table_level2_saf_smi_ansp_pdf1"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

```{r table_level2_saf_smi_ansp_pdf2}
mytable <-"table_level2_saf_smi_ansp_pdf2"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_level2_saf_smi_ansp_pdf1, hspace = 0, left_margin = 0, width = 1)`

\vspace*{-0.5cm}

`r layout_summary_table(table_level2_saf_smi_ansp_pdf2, hspace = 0, left_margin = 0, width = 1)`


\needspace{3\baselineskip}


\biggertext{Focus on separation minima}

`r saf_smi_text`

\needspace{2\baselineskip}

## Quality of occurences reporting 

`r saf_qr_text`

\needspace{2\baselineskip}

