[Annual Monitoring Report {{< var doc.year_report >}} - SES RP3]{.fakeh1}

## Contextual information
```{r fetch-data-ses, eval=TRUE}
data_context <-read_xlsx(
  paste0(data_folder, "SES.xlsx"),
  sheet = "Context",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() %>% 
  filter(year_report == .env$year_report & year == .env$year_report)

acc_no <- data_context %>% select(number_of_acc) %>% pull()
no_apt_big <- data_context %>% select(no_apts_big) %>% pull()
no_apt_small <- data_context %>% select(no_apts_small) %>% pull()

ert_trm_share <- data_context %>% select(ert_trm_share) %>% pull()
ert_cz <- data_context %>% select(ert_cz) %>% pull()
trm_cz <- data_context %>% select(trm_cz) %>% pull()

main_ansp <- data_context %>% select(main_ans_ps_ert) %>% pull()
other_ansp <- data_context %>% select(other_ans_ps_ert) %>% pull()
met_ansp <- data_context %>% select(met_providers) %>% pull()
```


::: columns
<!-- ******************* 1st column -->
:::: {.column width="34%"}
**No of ACCs  ** `r acc_no`

::::: columns
:::::: {.column width="60%"}
**No of airports in the scope of the performance plan**
::::::

:::::: {.column width="40%"}
**≥80'K    ** `r no_apt_big`<br/> **<80'K     ** `r no_apt_small`
::::::
:::::
::::

<!-- ******************* 2nd column -->
:::: {.column width="38%"}

**Share en route / terminal costs `r year_report` ** `r ert_trm_share`

::::: columns
:::::: {.column width="55%"}
**En route charging zone(s)**
::::::

:::::: {.column width="45%"}
`r ert_cz`
::::::
:::::

::::: columns
:::::: {.column width="55%"}
[**Terminal charging zone(s)**]{.context-text}
::::::

:::::: {.column width="45%"}
`r trm_cz`
::::::
:::::
::::

<!-- ******************* 3rd column -->
:::: {.column width="28%"}
::::: columns
:::::: {.column width="70%"}
**No of main ANSPs ** 
::::::

:::::: {.column width="30%"}
`r main_ansp`
::::::
:::::

::::: columns
:::::: {.column width="70%"}
**No of other ANSPs **
::::::

:::::: {.column width="30%"}
`r other_ansp`
::::::
:::::

::::: columns
:::::: {.column width="70%"}
**No of MET Providers **
::::::

:::::: {.column width="30%"}
`r met_ansp`
::::::
:::::

::::
:::


## Main PRB findings - {{< var doc.year_report >}}

```{r main-concl}
tsu_conc <- read_mytable("PRB_findings.xlsx", "main", "Table_Findings_main") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

main_conc1 <- tsu_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '') %>%  str_replace_all('@', '') 
```

`r main_conc1`

## Traffic (SES RP3 area)

::: {#container-mvt}
:::: {#chart-mvt class="mychart"}
```{r chart-mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "100%"
```
::::

:::: {#concl-mvt}
```{r concl-mvt}
mvt_conc <- read_mytable("PRB_findings.xlsx", "traffic_IFR", "Table_Findings_traffic_IFR") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

mvt_conc1 <- mvt_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '') 
```

`r mvt_conc1`
::::
:::

::: {#container-su style="clear: both"}

<br>

:::: {#chart-su class="mychart"}
```{r chart-su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "100%"
```
::::

:::: {#concl-su}
```{r concl-su}
tsu_conc <- read_mytable("PRB_findings.xlsx", "traffic_SUs", "Table_Findings_traffic_TSU") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

tsu_conc1 <- tsu_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '') 
```

`r tsu_conc1`
::::
:::

::: {#container-saf style="clear: both"}

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Safety (SES RP3 area)
:::: {#chart-saf class="mychart"}
```{r chart-saf}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```
::::

:::: {#concl-saf}
```{r concl-saf}
saf_conc <- read_mytable("PRB_findings.xlsx", "safety", "Table_Findings_safety") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

saf_conc1 <- saf_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n') 
```

`r saf_conc1`
::::
:::

::: {#container-env style="clear: both"}

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Environment (SES RP3 area)

:::: {#chart-env class="mychart"}
```{r chart-env}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```
::::

:::: {#concl-env}
```{r concl-env}
env_conc <- read_mytable("PRB_findings.xlsx", "environment", "Table_Findings_environment") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

env_conc1 <- env_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n') 
```

`r env_conc1`
::::
:::

::: {#container-cap style="clear: both"}

## Capacity (SES RP3 area)
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

:::: {#chart-cap class="mychart"}
```{r chart-cap, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
::::

:::: {#concl-cap}
```{r concl-cap}
cap_er_conc <- read_mytable("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

cap_er_conc1 <- cap_er_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n') 
```

`r cap_er_conc1`
::::
:::


::: {#container-cef style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Cost-efficiency (SES RP3 area)

:::: {#chart-cef class="mychart"}
```{r chart-cef}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```
::::

:::: {#concl-cef}
```{r concl-cef}
cef_conc <- read_mytable("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF") %>% 
  filter(Year_Report == year_report, State == 'SES') %>% 
  select(Conclusion) %>% toString() %>% paste0(., "@")

cef_conc1 <- cef_conc %>% str_replace_all(c('", ' = '\n\n', '\"' = '', '\n\n\n' = '\n\n')) %>% str_replace(fixed('c('), '') %>%  str_replace(fixed(')@'), '\n') 
```

`r cef_conc1`
::::
:::

