<!-- ### En route performance -->
<!-- #### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2) -->

```{r chart_env_kea_l2, options = (doclevel=c("level2")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart_env_kea_month, include=FALSE}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```

```{r chart_env_kep_scr, include=FALSE}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart_env_kep_scr_month, include=FALSE}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```


<!-- ### En route performance -->
<!-- #### En route ATFM delay (KPI#1) -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
<!-- #### Other indicators -->

```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_sector_opening_ses, include=FALSE}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```

<!-- #### Arrival ATFM delay (KPI#2) -->
```{r chart_cap_trm_l2, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm_month, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route charging zone -->
```{r chart_cef_duc_er_ses, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_su, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```

```{r chart_cef_cost, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```

```{r table_cef_cost, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cost"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- AUCU -->
```{r chart_cef_aucu, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```

```{r table_cef_aucu, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_aucu"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

```{r chart_cef_cex, R.options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```

```{r table_cef_cex, R.options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cex"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- regulatory result -->
```{r chart_cef_reg_res, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu,  options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```

## Environment - SES RP3

### PRB monitoring
```{r}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
```

`r env_conc1`

### En route performance

#### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2)

`r layout_2fig("chart_env_kea_l2", "chart_env_kea_month")`

`r layout_2fig("chart_env_kep_scr", "chart_env_kep_scr_month")`

#### Summary of performance at local level

```{r table_kea_summary}
mytable <-"table_env_kea_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_env_kea_all_states)`


## Capacity - SES RP3

### PRB monitoring

```{r cap_prb}
  cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r cap_er_conc1`

### En route performance

#### En route ATFM delay (KPI#1)

`r layout_2fig("chart_cap_er_l2", "chart_cap_er_month")`

```{r chart_cap_delay_bin}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

#### Summary of performance at local level

```{r table_cap_erdelay_summary}
mytable <-"table_cap_erdelay_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_cap_erdelay_all_states)`

#### Other indicators

`r layout_2fig("chart_cap_atco", "chart_cap_sector_opening_ses")`

### Terminal performance

#### Arrival ATFM delay (KPI#2)

`r layout_2fig("chart_cap_trm_l2", "chart_cap_trm_month")`

#### Summary of performance at local level

```{r table_cap_arrdelay_summary}
mytable <-"table_cap_arrdelay_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_cap_arrdelay_all_states)`

#### Other terminal performance indicators (PI#1-3)

```{r chart_cap_all_causes_delay_ses}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

## Cost-efficiency - SES RP3

### PRB monitoring

:::: {#concl-cef-duc}
```{r concl_cef_duc}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```
::::

`r cef_conc1`

### En route charging zone

`r layout_2fig("chart_cef_duc_er_ses", "chart_cef_su")`

`r layout_fig_table("chart_cef_cost", table_level2_cef_cost, vspace = -3.8)`


#### Summary of performance at local level

:::: {#table-cef-summary}
```{r table_cef_summary, options = (cztype="enroute")}
#| file: R/table_cef_summary.R
#| out.width: "100%"
#| fig-asp: 1
```
::::


#### Actual unit cost incurred by the users (AUCU) (PI#1)

`r layout_fig_table("chart_cef_aucu", table_level2_cef_aucu, vspace = -1.5)`

`r layout_fig_table("chart_cef_cex", table_level2_cef_cex, vspace = -2)`

#### Regulatory result (RR)

`r layout_2fig("chart_cef_reg_res", "chart_cef_reg_res_aucu")`

`r layout_2fig("chart_cef_reg_res_ansp", "chart_cef_net_res_main_ansp")`

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
\clearpage
\thispagestyle{empty} % Remove headers and footers from the final page
\begin{center}
\vspace*{\fill} % Center the text vertically
{\fontsize{20pt}{24pt}\selectfont \textbf{End of document}}
\vspace*{\fill}
\end{center}
```
