
```{r fetch-data-state, eval=TRUE}
pp_version <- params$pp_version
acc_no <- params$acc_no
acc_list <- params$acc_list
acc1 <- params$acc1
acc2 <- params$acc2
acc3 <- params$acc3
acc4 <- params$acc4
acc5 <- params$acc5
no_apt_big <- params$no_apt_big
no_apt_small <- params$no_apt_small

nat_curr <- params$nat_curr
xrate2017 <- params$xrate2017
tsu_share <- params$tsu_share
ert_cost_share <- params$ert_cost_share
ert_trm_share <- params$ert_trm_share

main_ansp <- params$main_ansp
other_ansps_str <- params$other_ansps_str
other_met_str <- params$other_met_str

```

```{r yearly_xrates}
# get yearly xrates

xrate <- get_xrates("enroute", ecz_list$ecz_id[1]) |> 
  filter(year == year_report) |> 
  select(pp_exchangerate)

xrate_year_report <- if_else(country == "Luxembourg", 1, pull(xrate))

```


# OVERVIEW

## Contextual information
*`r pp_version`*

```{=latex}

\begin{figure}

\footnotesize

\begin{minipage}[t]{0.31\linewidth}
```

**List of ACCs     ** `r acc_no`  
\hspace*{2em} `r acc1` `r ifelse(acc2 != "", "  ", "")`
`r ifelse(acc2 != "", "\\hspace*{2em}", "")` `r acc2` `r ifelse(acc3 != "", "  ", "")`
`r ifelse(acc3 != "", "\\hspace*{2em}", "")` `r acc3` `r ifelse(acc4 != "", "  ", "")`
`r ifelse(acc4 != "", "\\hspace*{2em}", "")` `r acc4` `r ifelse(acc5 != "", "  ", "")`
`r ifelse(acc5 != "", "\\hspace*{2em}", "")` `r paste0(acc5, "  ")` 

\vspace*{1em}
**No of airports in the scope**  
**of the performance plan:**  
\hspace*{2em} • **≥80'K     ** `r no_apt_big`  
\hspace*{2em} • **<80'K     ** `r no_apt_small`

```{=latex}
\end{minipage}%
%
\begin{minipage}[t]{0.38\linewidth}
```

**Exchange rate (1 EUR=)**  
\hspace*{2em} `r paste0("2017: ", xrate2017, " ", nat_curr, "  ")` 
\hspace*{2em} `r paste0(year_report, ": ", xrate_year_report, " ", nat_curr, "  ")`

\vspace*{0.5em}**Share of Union-wide:**  
\hspace*{2em} • **traffic (TSUs) `r year_report`  **  `r paste0(tsu_share, "  ")` 
\hspace*{2em} • **en route costs `r year_report` ** `r paste0(ert_cost_share, "  ")` 
**Share en route / terminal**  
**costs `r year_report`                    ** `r paste0(ert_trm_share, "  ")` 

\vspace*{0.5em}**En route charging zone(s)**
```{r ecz_list_string}
ecz_list_string <- paste0(
  fixed('`\\hspace*{2em}`{=tex}'),
  ecz_list$ecz_name[1],
  if_else(is.na(ecz_list$ecz_name[2]), '' ,  paste0(fixed('` \\\\ \\hspace*{2em}`{=tex}'), ecz_list$ecz_name[2])
          )
)
```
`r paste0(ecz_list_string, "  ")` 

**Terminal charging zone(s)**  
```{r tcz_list_string}
tcz_list_string <- if_else(no_tcz == 0, '`\\hspace*{2em}`{=tex} --',
paste0(
  fixed('`\\hspace*{2em}`{=tex}'),
  tcz_list$tcz_name[1],
  if_else(is.na(tcz_list$tcz_name[2]), '' , paste0(fixed('`\\\\ \\hspace*{2em}`{=tex}'), tcz_list$tcz_name[2])
  )
  ))
```

`r tcz_list_string`

```{=latex}
\end{minipage}%
%
\begin{minipage}[t]{0.31\linewidth}
```

```{r ansp_list_strings}
# this is very convoluted but I couldnt find any other way
other_ansps_list <- str_split(other_ansps_str, "<br/>")[[1]] %>%
  discard(~ .x == "")

other_ansps_str_1 <- reduce(other_ansps_list, ~ paste(.x, .y, sep = fixed('`\\\\`{=tex}\\hspace*{1.2em}')))

other_met_list <- str_split(other_met_str, "<br/>")[[1]] %>%
  discard(~ .x == "")

other_met_str_1 <- reduce(other_met_list, ~ paste(.x, .y, sep = fixed('`\\\\`{=tex}\\hspace*{1.2em}')))

```


**Main ANSP**  
\hspace*{1em} • `r paste0(main_ansp, "  ")`  

\vspace*{1em}**Other ANSPs**
`\begin{flushleft}`{=tex}
\vspace*{-1em}\hspace*{1em} `r paste0(other_ansps_str_1, "  ")` 
`\end{flushleft}`{=tex}

**MET Providers**
`\begin{flushleft}`{=tex}
\vspace*{-1em}\hspace*{1em} `r other_met_str_1`
`\end{flushleft}`{=tex}

```{=latex}
\end{minipage}%

\end{figure}%
```


## Traffic (En route traffic zone)

```{r mvt_conc}
mvt_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_IFR", "Table_Findings_traffic_IFR")

mvt_text <- break_l1_text(mvt_conc1) 
mvt_text1 <- mvt_text$text1
mvt_text2 <- mvt_text$text2
```

```{r chart_level1_traffic_mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r mvt_conc1`

```{r su_conc1}
tsu_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_SUs", "Table_Findings_traffic_TSU")

tsu_text <- break_l1_text(tsu_conc1) 
tsu_text1 <- tsu_text$text1
tsu_text2 <- tsu_text$text2
```

```{r chart_level1_traffic_su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r tsu_conc1`

## Safety (Main ANSP)

```{r saf_conc1}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

```{r chart_saf_l1, options = (saf_ansp_index = 1)}
#| file: R/chart_level1_saf.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r saf_conc1`

<!-- exception for luxembourg -->
`r if (params$country == "Luxembourg") "::: {.content-hidden}"`

## Environment (Member State)

```{r concl_env}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
```

```{r chart_env_kea_l1, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r env_conc1`

`r if (params$country == "Luxembourg") ":::"`

## Capacity (Member State)

```{r concl_cap}
cap_er_conc1 <-  get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
cap_trm_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "TRM_capacity", "Table_Findings_TRM_capacity")

cap_conc1 <- paste0(if_else(cap_er_conc1 == "character(0\n", "", paste0(cap_er_conc1, "\n\n")), if_else(cap_trm_conc1 == "NA" | stringr::str_detect(cap_trm_conc1, "character"), "", cap_trm_conc1))
```

```{r chart_cap_er, options = (cztype=c("enroute")), include = (params$country != "Luxembourg")}
#| file: R/chart_level1_cap.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r if_else(params$country != "Luxembourg", cap_er_conc1, '')`

```{r chart_cap_trm, options = (cztype=c("terminal")), include = params$no_tcz != 0}
#| file: R/chart_level1_cap.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r if_else(params$no_tcz != 0, cap_trm_conc1, '')`

## Cost-efficiency (En route/Terminal charging zone(s))

```{r concl-cef}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```

```{r chart_cef_er_1, options = (cz=c("1", "enroute", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r chart_cef_er_2, options = (cz=c("2", "enroute", "level1")), eval = (params$no_ecz == 2)}
#| file: R/chart_level1_cef.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r chart_cef_trm_1, options = (cz=c("1", "terminal", "level1")), eval = (params$no_tcz != 0)}
#| file: R/chart_level1_cef.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r chart_cef_trm_2, options = (cz=c("2", "terminal", "level1")), eval = (params$no_tcz == 2)}
#| file: R/chart_level1_cef.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r cef_conc1`

